---
title: "ANOVA"
date: "2019-05-09"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

Purpose of this file:

   1. Conduct ANOVA's to get effect size study design

# Packages and Set-Up

```{r set-up, tidy=T}
##Chunk iptions
knitr::opts_chunk$set(out.width="225%")

#setwd('C:/Users/noahp/Dropbox/MCFA Thesis/Code Results')

## Packages
## General Packages
library(tidyverse)
library(car)
library(psych)
# Formatting and Tables
library(kableExtra)
library(xtable)
# For plotting
library(ggplot2)
theme_set(theme_bw())
# Data manipulating
library(dplyr)

## One global parameter for printing figures
save.fig <- F

## Load up the functions needed for ANOVA and Assumption checking
source('code/r_functions.R')

```


# Data Management

```{r data, tidy=T}

sim_results <- as_tibble(read.table('data/compiled_fit_results.txt', header=T,sep='\t'))

## Next, turn condition into a factor for plotting
sim_results$Condition <- as.factor(sim_results$Condition)

## Next, since TLI is non-normed, any value greater than 1 needs to be rescaled to 1.
sim_results$TLI <- ifelse(sim_results$TLI > 1, 1, sim_results$TLI)
sim_results$TLI <- ifelse(sim_results$TLI < 0, 0, sim_results$TLI)
## Next, summarize the results of the chi-square test of model fit. This is done simply by comparing the p-value to alpha (0.05) and indicating whether the model was flagged as fitting or not.
# Note: if  p < 0.05 then this variable is flagged as 0, and 1 otherwise
sim_results$Chi2_pvalue_decision <- ifelse(sim_results$chisqu_pvalue > 0.05, 1, 0)
# 0 = rejected that these data fit this model
# 1 = failed to reject that these data fit this model

## Need to make codes for the ROC analyses outcomes
# first, C vs. M1,M2,M12 - Perfect specification
sim_results$C <- ifelse(sim_results$Model == 'C', 1, 0)
# second, C|M2 vs. M1|M12- correct level 1 model
sim_results$C_Level_1 <- ifelse(sim_results$Model == 'C' | sim_results$Model == 'M2', 1, 0)
# third, C|M1 vs. M2|M12- correct level 2 model
sim_results$C_Level_2 <- ifelse(sim_results$Model == 'C' | sim_results$Model == 'M1', 1, 0)
```

## Adding Labels to Conditions

Currently, each condition is kind of like a hidden id that we don't know what the actual factor is. 
So, first thing isto create meaningful labels for us to use.
Remember, the 72 conditions for the this study were

  1. Level-1 sample size (5, 10, 30)
  2. Level-2 sample size (30, 50, 100, 200)
  3. Observed indicator ICC (.1, .3, .5)
  4. Latent variable ICC (.1, .5)
  
```{r}
## level-1 Sample size
ss_l1 <- c(5, 10, 30) ## 6 conditions each
ss_l2 <- c(30, 50, 100, 200) ## 18 condition each
icc_ov <- c(.1, .3, .5) ## 2 conditions each
icc_lv <- c(.1, .5) ## every other condition
nCon <- 72 # number of conditions
nRep <- 500 # number of replications per condition
nMod <- 12 ## numberof estimated models per conditions
## Total number of rows: 432,000
ss_l2 <- c(rep(ss_l2[1], 18*nRep*nMod), rep(ss_l2[2], 18*nRep*nMod), rep(ss_l2[3], 18*nRep*nMod), rep(ss_l2[4], 18*nRep*nMod))
ss_l1 <- rep(c(rep(ss_l1[1],6*nRep*nMod), rep(ss_l1[2],6*nRep*nMod), rep(ss_l1[3],6*nRep*nMod)), 4)
icc_ov <- rep(c(rep(icc_ov[1], 2*nRep*nMod), rep(icc_ov[2], 2*nRep*nMod), rep(icc_ov[3], 2*nRep*nMod)), 12)
icc_lv <- rep(c(rep(icc_lv[1], nRep*nMod), rep(icc_lv[2], nRep*nMod)), 36)
## Force these vectors to be column vectors
ss_l1 <- matrix(ss_l1, ncol=1)
ss_l2 <- matrix(ss_l2, ncol=1)
icc_ov <- matrix(icc_ov, ncol=1)
icc_lv <- matrix(icc_lv, ncol=1)
## Add the labels to the results data frame
sim_results <- sim_results[order(sim_results$Condition),]
sim_results <- cbind(sim_results, ss_l1, ss_l2, icc_ov, icc_lv)

## Force the conditions to be factors
sim_results$ss_l1 <- as.factor(sim_results$ss_l1)
sim_results$ss_l2 <- as.factor(sim_results$ss_l2)
sim_results$icc_ov <- as.factor(sim_results$icc_ov)
sim_results$icc_lv <- as.factor(sim_results$icc_lv)
sim_results$Model <- factor(sim_results$Model, levels = c('C','M1','M2','M12'), ordered = T)

## Subset to the usable cases
sim_results <- filter(sim_results, Converge == 1 & Admissible == 1)
```

# ANOVA and effect sizes for distributional differences

One of the key outcomes for this large simulation was how the distribution of fit indices changes due to manipulating the design factor. 
So, for this simulation experiment, there were 6 factors systematically varied.
Of these 6 factors, 4 were factors influencing the observed data and 2 were factors pertaining to estimation and model fitting.
The factors were

  1. Level-1 sample size (5, 10, 30)
  2. Level-2 sample size (30, 50, 100, 200)
  3. Observed indicator ICC (.1, .3, .5)
  4. Latent variable ICC (.1, .5)
  5. Model specification (C, M1, M2, M12)
  6. Model estimator (MLR, ULSMV, WLSMV)
  
For each fit statistic, an analysis of variance (ANOVA) was conducted in order to test how much influence each of these design factors had on the distribution of the fit indice.

General Linear Model investigated for fit measures was: 
\[
Y_{ijklmno} = \mu + \alpha_{j} + \beta_{k} + \gamma_{l} + \delta_m + \zeta_n + \theta_o +\\
(\alpha\beta)_{jk} + (\alpha\gamma)_{jl}+ (\alpha\delta)_{jm} + (\alpha\zeta)_{jn} + (\alpha\theta)_{jo}+ \\
(\beta\gamma)_{kl}+ (\beta\delta)_{km} + (\beta\zeta)_{kn} + (\beta\theta)_{ko}+ (\gamma\delta)_{lm} +\\ 
(\gamma\zeta)_{ln} + (\gamma\theta)_{lo} +(\delta\zeta)_{mn} + (\delta\theta)_{mo} + (\zeta\theta)_{no} + \varepsilon_{ijklmno}
\]
where 

  1. $\mu$ is the grand mean,
  2. $\alpha_{j}$ is the effect of Level-1 sample size,  
  3. $\beta_{k}$ is the effect of Level-2 sample size, 
  4. $\gamma_{l}$ is the effect of Observed indicator ICC, 
  5. $\delta_m$ is the effect of Latent variable ICC, 
  6. $\zeta_n$ is the effect of Model specification, 
  7. $\theta_o$ is the effect of Model estimator , 
  8. $(\alpha\beta)_{jk}$ is the interaction between  Level-1 sample size and Level-2 sample size,
  9. $(\alpha\gamma)_{jl}$ is the interaction between Level-1 sample size and Observed indicator ICC,
  10. $(\alpha\delta)_{jm}$ is the interaction between  Level-1 sample size and Latent variable ICC,
  11. $(\alpha\zeta)_{jn}$ is the interaction between  Level-1 sample size and Model specification,
  12. $(\alpha\theta)_{jo}$ is the interaction between  Level-1 sample size and Model estimator ,
  13. $(\beta\gamma)_{kl}$ is the interaction between  Level-2 sample size and Observed indicator ICC,
  14. $(\beta\delta)_{km}$ is the interaction between  Level-2 sample size and Latent variable ICC,
  15. $(\beta\zeta)_{kn}$ is the interaction between  Level-2 sample size and Model specification,
  16. $(\beta\theta)_{ko}$ is the interaction between  Level-2 sample size and Model estimator ,
  17. $(\gamma\delta)_{lm}$ is the interaction between Observed indicator ICC and Latent variable ICC,
  18. $(\gamma\zeta)_{ln}$ is the interaction between  Observed indicator ICC and Model specification,
  19. $(\gamma\theta)_{lo}$ is the interaction between  Observed indicator ICC and Model estimator ,
  20. $(\delta\zeta)_{mn}$ is the interaction between  Latent variable ICC and Model specification,
  21. $(\delta\theta)_{mo}$ is the interaction between  Latent variable ICC and Model estimator ,
  22. $(\zeta\theta)_{no}$ is the interaction between Model specification and Model estimator , and
  23. $\varepsilon_{ijkl}$ is the residual error for the $i^{th}$ observed fit measure.
  
  
Note that for most of these terms there are actually 2 or 3 terms actually estimated.
These additional terms are because of the categorical natire of each effect so we have to create "reference" groups and calculate the effect of being in a group other than the reference group. 
Higher order interactions were omitted for clearity of interpretation of the model.
If interested in higher-order interactins, please see Maxwell and Delaney (2004).

The real reason the higher order interaction was omitted:
Because I have no clue how to interpret a 6-way interaction (whatever the heck that is), I am limiting the ANOVA to all bivariate interactions.


Diagnostics for factorial ANOVA:

1. Independence of Observations
2. Normality of residuals across cells for the design
3. Homogeneity of variance across cells

Independence of observations is by design, where these data were randomly generated from a known population and observations are across replications and are independent.
The normality assumptions is that the residuals of the models are normally distributed across the design cells. 
The normality assumption is tested by investigation by Shapiro-Wilks Test, the K-S test, and visual inspection of  QQ-plots and histograms. 
The equality of variance is checked through Levene's test across all the different conditions/groupings. 
Furthermore, the plots of the residuals are also indicative of the equality of variance across groups as there should be no apparent pattern to the residual plots. 

## Assumption Checking

### CFI 

```{r anova-CFI}
## model factors...
flist <- c('ss_l1', 'ss_l2', 'icc_ov', 'icc_lv','Model', 'Estimator')
## Check assumptions
anova_assumptions_check(
  sim_results, 'CFI', factors = flist,
  model = as.formula('CFI ~ ss_l1 + ss_l2 + icc_ov + icc_lv + Model + Estimator + ss_l1:ss_l2 + ss_l1:icc_ov + ss_l1:icc_lv + ss_l1:Model + ss_l1:Estimator + ss_l2:icc_ov + ss_l2:icc_lv + ss_l2:Model + ss_l2:Estimator + icc_ov:icc_lv + icc_ov:Model + icc_ov:Estimator + icc_lv:Model + icc_lv:Estimator + Model:Estimator'))

```

### TLI

```{r anova-tli}
anova_assumptions_check(
  sim_results, 'TLI', factors = flist,
  model = as.formula('TLI ~ ss_l1 + ss_l2 + icc_ov + icc_lv + Model + Estimator + ss_l1:ss_l2 + ss_l1:icc_ov + ss_l1:icc_lv + ss_l1:Model + ss_l1:Estimator + ss_l2:icc_ov + ss_l2:icc_lv + ss_l2:Model + ss_l2:Estimator + icc_ov:icc_lv + icc_ov:Model + icc_ov:Estimator + icc_lv:Model + icc_lv:Estimator + Model:Estimator'))
```

### RMSEA

```{r anova-RMSEA}
anova_assumptions_check(
  sim_results, 'RMSEA', factors = flist,
  model = as.formula('RMSEA ~ ss_l1 + ss_l2 + icc_ov + icc_lv + Model + Estimator + ss_l1:ss_l2 + ss_l1:icc_ov + ss_l1:icc_lv + ss_l1:Model + ss_l1:Estimator + ss_l2:icc_ov + ss_l2:icc_lv + ss_l2:Model + ss_l2:Estimator + icc_ov:icc_lv + icc_ov:Model + icc_ov:Estimator + icc_lv:Model + icc_lv:Estimator + Model:Estimator'))
```


### SRMRW

```{r anova-SRMRW}
anova_assumptions_check(
  sim_results, 'SRMRW', factors = flist,
  model = as.formula('SRMRW ~ ss_l1 + ss_l2 + icc_ov + icc_lv + Model + Estimator + ss_l1:ss_l2 + ss_l1:icc_ov + ss_l1:icc_lv + ss_l1:Model + ss_l1:Estimator + ss_l2:icc_ov + ss_l2:icc_lv + ss_l2:Model + ss_l2:Estimator + icc_ov:icc_lv + icc_ov:Model + icc_ov:Estimator + icc_lv:Model + icc_lv:Estimator + Model:Estimator'))
```


### SRMRB

```{r anova-srmrb}
anova_assumptions_check(
  sim_results, 'SRMRB', factors = flist,
  model = as.formula('SRMRB ~ ss_l1 + ss_l2 + icc_ov + icc_lv + Model + Estimator + ss_l1:ss_l2 + ss_l1:icc_ov + ss_l1:icc_lv + ss_l1:Model + ss_l1:Estimator + ss_l2:icc_ov + ss_l2:icc_lv + ss_l2:Model + ss_l2:Estimator + icc_ov:icc_lv + icc_ov:Model + icc_ov:Estimator + icc_lv:Model + icc_lv:Estimator + Model:Estimator'))
```

## ANOVA Analyses

### CFI

```{r anova-CFI-est}

model <- as.formula('CFI ~ ss_l1 + ss_l2 + icc_ov + icc_lv + Model + Estimator + ss_l1:ss_l2 + ss_l1:icc_ov + ss_l1:icc_lv + ss_l1:Model + ss_l1:Estimator + ss_l2:icc_ov + ss_l2:icc_lv + ss_l2:Model + ss_l2:Estimator + icc_ov:icc_lv + icc_ov:Model + icc_ov:Estimator + icc_lv:Model + icc_lv:Estimator + Model:Estimator')

fit <- aov(model, data = sim_results)
fit.out <- summary(fit)
fit.out
cfi.out <- cbind(omega2(fit.out),p_omega2(fit.out))
cfi.out


```

### TLI

```{r anova-tli-est}
model <- as.formula('TLI ~ ss_l1 + ss_l2 + icc_ov + icc_lv + Model + Estimator + ss_l1:ss_l2 + ss_l1:icc_ov + ss_l1:icc_lv + ss_l1:Model + ss_l1:Estimator + ss_l2:icc_ov + ss_l2:icc_lv + ss_l2:Model + ss_l2:Estimator + icc_ov:icc_lv + icc_ov:Model + icc_ov:Estimator + icc_lv:Model + icc_lv:Estimator + Model:Estimator')

fit <- aov(model, data = sim_results)
fit.out <- summary(fit)
fit.out
tli.out <- cbind(omega2(fit.out),p_omega2(fit.out))
tli.out
```

### RMSEA

```{r anova-RMSEA-est}
model <- as.formula('RMSEA ~ ss_l1 + ss_l2 + icc_ov + icc_lv + Model + Estimator + ss_l1:ss_l2 + ss_l1:icc_ov + ss_l1:icc_lv + ss_l1:Model + ss_l1:Estimator + ss_l2:icc_ov + ss_l2:icc_lv + ss_l2:Model + ss_l2:Estimator + icc_ov:icc_lv + icc_ov:Model + icc_ov:Estimator + icc_lv:Model + icc_lv:Estimator + Model:Estimator')

fit <- aov(model, data = sim_results)
fit.out <- summary(fit)
fit.out
rmsea.out <- cbind(omega2(fit.out),p_omega2(fit.out))
rmsea.out
```


### SRMRW

```{r anova-srmrw-est}
model <- as.formula('SRMRW ~ ss_l1 + ss_l2 + icc_ov + icc_lv + Model + Estimator + ss_l1:ss_l2 + ss_l1:icc_ov + ss_l1:icc_lv + ss_l1:Model + ss_l1:Estimator + ss_l2:icc_ov + ss_l2:icc_lv + ss_l2:Model + ss_l2:Estimator + icc_ov:icc_lv + icc_ov:Model + icc_ov:Estimator + icc_lv:Model + icc_lv:Estimator + Model:Estimator')

fit <- aov(model, data = sim_results)
fit.out <- summary(fit)
fit.out
srmrw.out <- cbind(omega2(fit.out),p_omega2(fit.out))
srmrw.out
```


### SRMRB

```{r anova-srmrb-est}
model <- as.formula('SRMRB ~ ss_l1 + ss_l2 + icc_ov + icc_lv + Model + Estimator + ss_l1:ss_l2 + ss_l1:icc_ov + ss_l1:icc_lv + ss_l1:Model + ss_l1:Estimator + ss_l2:icc_ov + ss_l2:icc_lv + ss_l2:Model + ss_l2:Estimator + icc_ov:icc_lv + icc_ov:Model + icc_ov:Estimator + icc_lv:Model + icc_lv:Estimator + Model:Estimator')

fit <- aov(model, data = sim_results)
fit.out <- summary(fit)
fit.out
srmrb.out <- cbind(omega2(fit.out),p_omega2(fit.out))
srmrb.out
```

## Summary Table of Effect Sizes

```{r sum-tab-eff}

tb <- cbind(cfi.out, tli.out, rmsea.out, srmrw.out, srmrb.out)

kable(tb, format='html') %>%
    kable_styling(full_width = T) %>%
    add_header_above(c('Effect'=1,'CFI'=2,'TLI'=2,'RMSEA'=2,'SRMRW'=2,'SRMRB'=2))

## Print out in tex
print(xtable(tb, digits = 3), booktabs = T, include.rownames = T)


## Table of partial-omega2
tb <- cbind(cfi.out[,2, drop=F], tli.out[,2, drop=F], rmsea.out[,2, drop=F], srmrw.out[,2, drop=F], srmrb.out[,2, drop=F])

kable(tb, format='html') %>%
    kable_styling(full_width = T) %>%
    add_header_above(c('Effect'=1,'CFI'=1,'TLI'=1,'RMSEA'=1,'SRMRW'=1,'SRMRB'=1))

## Print out in tex
print(xtable(tb, digits = 3), booktabs = T, include.rownames = T)


## Table of omege-2

tb <- cbind(cfi.out[,1, drop=F], tli.out[,1, drop=F], rmsea.out[,1, drop=F], srmrw.out[,1, drop=F], srmrb.out[,1, drop=F])

kable(tb, format='html') %>%
    kable_styling(full_width = T) %>%
    add_header_above(c('Effect'=1,'CFI'=1,'TLI'=1,'RMSEA'=1,'SRMRW'=1,'SRMRB'=1))

## Print out in tex
print(xtable(tb, digits = 3), booktabs = T, include.rownames = T)

```

