---
title: "ROC Analyses"
date: "2019-05-09"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---


Purpose of this file:

   1. Conduct ROC Analysies
   2. Create ROC Curves
   3. Create Summary tables of ROC analyses

# Packages and Set-Up

```{r set-up, tidy=T}
##Chunk iptions
knitr::opts_chunk$set(out.width="225%")

#setwd('C:/Users/noahp/Dropbox/MCFA Thesis/Code Results')

## Packages
## General Packages
library(tidyverse)
library(car)
library(psych)
# Formatting and Tables
library(kableExtra)
library(xtable)
# For plotting
library(ggplot2)
theme_set(theme_bw())
# Data manipulating
library(dplyr)
# ROC Analysis
library(pROC)

## One global parameter for printing figures
save.fig <- F

## Load up the functions needed for ANOVA and Assumption checking
source('code/r_functions.R')

```


# Data Management

```{r data, tidy=T}

sim_results <- as_tibble(read.table('data/compiled_fit_results.txt', header=T,sep='\t'))

## Next, turn condition into a factor for plotting
sim_results$Condition <- as.factor(sim_results$Condition)

## Next, since TLI is non-normed, any value greater than 1 needs to be rescaled to 1.
sim_results$TLI <- ifelse(sim_results$TLI > 1, 1, sim_results$TLI)
sim_results$TLI <- ifelse(sim_results$TLI < 0, 0, sim_results$TLI)
## Next, summarize the results of the chi-square test of model fit. This is done simply by comparing the p-value to alpha (0.05) and indicating whether the model was flagged as fitting or not.
# Note: if  p < 0.05 then this variable is flagged as 0, and 1 otherwise
sim_results$Chi2_pvalue_decision <- ifelse(sim_results$chisqu_pvalue > 0.05, 1, 0)
# 0 = rejected that these data fit this model
# 1 = failed to reject that these data fit this model

## Need to make codes for the ROC analyses outcomes
# first, C vs. M1,M2,M12 - Perfect specification
sim_results$C <- ifelse(sim_results$Model == 'C', 1, 0)
# second, C|M2 vs. M1|M12- correct level 1 model
sim_results$C_Level_1 <- ifelse(sim_results$Model == 'C' | sim_results$Model == 'M2', 1, 0)
# third, C|M1 vs. M2|M12- correct level 2 model
sim_results$C_Level_2 <- ifelse(sim_results$Model == 'C' | sim_results$Model == 'M1', 1, 0)
```

## Adding Labels to Conditions

Currently, each condition is kind of like a hidden id that we don't know what the actual factor is. 
So, first thing isto create meaningful labels for us to use.
Remember, the 72 conditions for the this study were

  1. Level-1 sample size (5, 10, 30)
  2. Level-2 sample size (30, 50, 100, 200)
  3. Observed indicator ICC (.1, .3, .5)
  4. Latent variable ICC (.1, .5)
  
```{r}
## level-1 Sample size
ss_l1 <- c(5, 10, 30) ## 6 conditions each
ss_l2 <- c(30, 50, 100, 200) ## 18 condition each
icc_ov <- c(.1, .3, .5) ## 2 conditions each
icc_lv <- c(.1, .5) ## every other condition
nCon <- 72 # number of conditions
nRep <- 500 # number of replications per condition
nMod <- 12 ## numberof estimated models per conditions
## Total number of rows: 432,000
ss_l2 <- c(rep(ss_l2[1], 18*nRep*nMod), rep(ss_l2[2], 18*nRep*nMod), rep(ss_l2[3], 18*nRep*nMod), rep(ss_l2[4], 18*nRep*nMod))
ss_l1 <- rep(c(rep(ss_l1[1],6*nRep*nMod), rep(ss_l1[2],6*nRep*nMod), rep(ss_l1[3],6*nRep*nMod)), 4)
icc_ov <- rep(c(rep(icc_ov[1], 2*nRep*nMod), rep(icc_ov[2], 2*nRep*nMod), rep(icc_ov[3], 2*nRep*nMod)), 12)
icc_lv <- rep(c(rep(icc_lv[1], nRep*nMod), rep(icc_lv[2], nRep*nMod)), 36)
## Force these vectors to be column vectors
ss_l1 <- matrix(ss_l1, ncol=1)
ss_l2 <- matrix(ss_l2, ncol=1)
icc_ov <- matrix(icc_ov, ncol=1)
icc_lv <- matrix(icc_lv, ncol=1)
## Add the labels to the results data frame
sim_results <- sim_results[order(sim_results$Condition),]
sim_results <- cbind(sim_results, ss_l1, ss_l2, icc_ov, icc_lv)

## Force the conditions to be factors
sim_results$ss_l1 <- as.factor(sim_results$ss_l1)
sim_results$ss_l2 <- as.factor(sim_results$ss_l2)
sim_results$icc_ov <- as.factor(sim_results$icc_ov)
sim_results$icc_lv <- as.factor(sim_results$icc_lv)
sim_results$Model <- factor(sim_results$Model, levels = c('C','M1','M2','M12'), ordered = T)

## Subset to the usable cases
sim_results <- filter(sim_results, Converge == 1 & Admissible == 1)
```

# Hit Rates

The cut-off values established by Hu and Bentler (1999) were determined
by an inspection of the hit rates of various cut-off criteria. In some conditions, the hit
rates were based on a rule with two different fit statistics. A hit rate is the proportion
of times the true (generating) model had a value on the fit index at or above the
cut-off. This is extremely valuable information, because knowing the lower bound
for plausible values of fit indices just due to random variation allows the creation of
guidelines for use of fit statistics. This is essential because many fit indices do not
have an easily derivable analytic distribution.


```{r}
## Need to subset to only the correctly specified model
mydata <- filter(sim_results, Model == "C")

## Set up results
ncut<-10
cut.low <- c(.9,.01)
cut.high <- c(.99,.1)
cutoff <- list()
cutoff[["CFI"]] <- cutoff[["TLI"]] <- seq(from=cut.low[1], to=cut.high[1], by=((.1)/ncut))
cutoff[["RMSEA"]] <- cutoff[["SRMRW"]] <- cutoff[["SRMRB"]] <- seq(from=cut.low[2], to=cut.high[2], by= ((.1)/ncut))

## Initialize results table
hit_rate_results <- as_tibble(as.data.frame(matrix(0,ncol=(1+ncut), nrow=5)))
colnames(hit_rate_results) <- c('Index', paste0(cutoff[["CFI"]], '/', paste0(cutoff[["RMSEA"]])))

## Start looping around cutoffs
INDEX <- c("CFI", "TLI", "RMSEA", "SRMRW", "SRMRB")
index <- "CFI"
i<- j <- 1
for(index in INDEX){
  for(j in 1:ncut){
    ## save ids
    hit_rate_results[i, 1] <- index
    ## figure out the diection of comparson
    dir <- ifelse(index == "CFI" | index == "TLI", ">", "<")
    ## Calc andsave hit rate
    hit_rate_results[i, (1+j)] <- hit_rate_calc(mydata[,index], cutoff[[index]][j], dir)
  }
  ## Update iterator for rows
  i <- i + 1
}


kable(hit_rate_results, format = 'html') %>%
  kable_styling(full_width = T)

print(xtable(hit_rate_results, digits=3), booktabs = T)
```

### Hit Rates by Estimator


```{r hit-con}

hit_rate_results <- as.data.frame(matrix(0,ncol=8))
colnames(hit_rate_results) <- c("Estimator", "CFI", "TLI", "RMSEA", "SRMRW", "SRMRB", "Cutoff.cfi", "Cutoff.rmsea")

## Start looping around cutoffs
j <- 1
for(j in 1:ncut){
    ## Calc hit rates
    hit <-  mydata %>%
        group_by(Estimator) %>%
        summarize(
          CFI = hit_rate_calc(CFI, cutoff[["CFI"]][j], ">"),
          TLI = hit_rate_calc(TLI, cutoff[["TLI"]][j], ">"),
          RMSEA = hit_rate_calc(RMSEA, cutoff[["RMSEA"]][j], "<"),
          SRMRW = hit_rate_calc(SRMRW, cutoff[["SRMRW"]][j], "<"),
          SRMRB = hit_rate_calc(SRMRB, cutoff[["SRMRB"]][j], "<"))
    hit$Cutoff.cfi <- cutoff[["CFI"]][j]
    hit$Cutoff.rmsea <- cutoff[["RMSEA"]][j]
    ## Calc andsave hit rate
    hit_rate_results <- rbind(hit_rate_results, hit)
} ## End ncuts iter
hit_rate_results<-hit_rate_results[-1,]


kable(hit_rate_results, format = 'html', row.names = F) %>%
  kable_styling(full_width = T)
print(xtable(hit_rate_results, digits = 3), booktabs=T, include.rownames = F)


## Some reformatting for plotting
h <- hit_rate_results
c <- unique(h$Cutoff.cfi)
d <- unique(h$Cutoff.rmsea)
h11<- h22 <- NULL
i <- 1
for(i in 1:10){

  h.cfi <- h[ h$Cutoff.cfi == c[i] , "CFI", drop = F]
  h.tli <- h[ h$Cutoff.cfi == c[i] , "TLI", drop = F]
  h.rmsea <- h[ h$Cutoff.rmsea == d[11-i] , "RMSEA", drop = F]
  h.srmrw <- h[ h$Cutoff.rmsea == d[11-i] , "SRMRW", drop = F]
  h.srmrb <- h[ h$Cutoff.rmsea == d[11-i] , "SRMRB", drop = F]
  colnames(h.cfi) <- colnames( h.tli) <-c[i]
  colnames(h.rmsea) <- colnames(h.srmrw) <- colnames(h.srmrb) <- d[11-i]
  h1 <- rbind(h.cfi, h.tli)
  h2 <- rbind(h.rmsea,h.srmrw,h.srmrb)

  if(i == 1) {
    a1 <- matrix(c(rep("CFI",3), rep("TLI",3)), ncol=1)
    a2 <- matrix(c(rep("RMSEA",3), rep("SRMRW",3), rep("SRMRB",3)), ncol=1)

    b1 <- matrix(rep(c("MLR", "ULSMV", "WLSMV"),2), ncol=1)
    b2 <- matrix(rep(c("MLR", "ULSMV", "WLSMV"),3), ncol=1)
    h11 <- cbind(b1,a1,h1)
    h22 <- cbind(b2,a2,h2)
  }
  if(i>1){
    h11 <- cbind(h11, h1)
    h22 <- cbind(h22, h2)
  }
}

kable(h11, format = 'html', row.names = F) %>%
  kable_styling(full_width = T)
print(xtable(h11, digits = 3), booktabs=T, include.rownames = F)


kable(h22, format = 'html', row.names = F) %>%
  kable_styling(full_width = T)
print(xtable(h22, digits = 3), booktabs=T, include.rownames = F)



```


## Hit Rates by Sample Sizes

```{r}

hit.list <- list()
## Start looping around cutoffs
j <- 1
for(j in 1:ncut){
    ## Calc hit rates
    hit <-  mydata %>%
        group_by(ss_l2, ss_l1) %>%
        summarize(
          CFI = hit_rate_calc(CFI, cutoff[["CFI"]][j], ">"),
          TLI = hit_rate_calc(TLI, cutoff[["TLI"]][j], ">"),
          RMSEA = hit_rate_calc(RMSEA, cutoff[["RMSEA"]][j], "<"),
          SRMRW = hit_rate_calc(SRMRW, cutoff[["SRMRW"]][j], "<"),
          SRMRB = hit_rate_calc(SRMRB, cutoff[["SRMRB"]][j], "<"))
    hit$Cutoff.cfi <- cutoff[["CFI"]][j]
    hit$Cutoff.rmsea <- cutoff[["RMSEA"]][j]
    hit.list[[j]] <- hit
    ## Calc andsave hit rate
    #hit_rate_results <- rbind(hit_rate_results, hit)
} ## End ncuts iter


hit_rate_results<-rbind(hit.list[[1]], hit.list[[2]], hit.list[[3]], hit.list[[4]], hit.list[[5]], hit.list[[6]], hit.list[[7]], hit.list[[8]], hit.list[[9]], hit.list[[10]])


kable(hit_rate_results, format = 'html') %>%
  kable_styling(full_width = T)
print(xtable(hit_rate_results, digits = 3), booktabs=T, include.rownames = F)


```


## Hit Rates by Sample Sizes

```{r}

hit.list <- list()
## Start looping around cutoffs
j <- 1
for(j in 1:ncut){
    ## Calc hit rates
    hit <-  mydata %>%
        group_by(ss_l2, ss_l1, icc_ov, icc_lv) %>%
        summarize(
          CFI = hit_rate_calc(CFI, cutoff[["CFI"]][j], ">"),
          TLI = hit_rate_calc(TLI, cutoff[["TLI"]][j], ">"),
          RMSEA = hit_rate_calc(RMSEA, cutoff[["RMSEA"]][j], "<"),
          SRMRW = hit_rate_calc(SRMRW, cutoff[["SRMRW"]][j], "<"),
          SRMRB = hit_rate_calc(SRMRB, cutoff[["SRMRB"]][j], "<"))
    hit$Cutoff.cfi <- cutoff[["CFI"]][j]
    hit$Cutoff.rmsea <- cutoff[["RMSEA"]][j]
    hit.list[[j]] <- hit
    ## Calc andsave hit rate
    hit_rate_results <- rbind(hit_rate_results, hit)
} ## End ncuts iter
hit_rate_results<-hit_rate_results[-1,]

kable(hit_rate_results, format = 'html') %>%
  kable_styling(full_width = T)
print(xtable(hit_rate_results, digits = 3), booktabs=T, include.rownames = F)


```


