---
title: "Descriptive Statistics, Tables and Boxplots"
author: "noah-padgett"
date: "2019-05-07"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

<!-- % 
%% ============================================= #
%%               Padgettt                
%% ============================================= #
%% Data Created: 2019-02-20
%% Date Modified: 2019-02-26
%% By: R. Noah Padgett                   
%% ============================================= #
%% MA Thesis Project                     
%% ============================================= #
%% Purpose:
%% This R script is for 
%%   1. creating simple descriptive statistics 
%%     across conditions
%%   2. Generating tables of those stats
%%   3. Create simple boxplots for trends
%%   4. Creating publication boxplots
%%
%% The output is numerous .eps files (figures)
%% and code for tables in latex
%% ============================================= # -->


Purpose of this file:

   1. creating simple descriptive statistics across conditions
   2. Generating tables of those stats
   3. Create simple boxplots for trends
   4. Creating publication boxplots

The output is numerous .eps files (figures) and code for tables in latex

# Packages and Set-Up

```{r set-up, tidy=T}
##Chunk iptions
knitr::opts_chunk$set(out.width = "225%")

#setwd('C:/Users/noahp/Dropbox/MCFA Thesis/Code Results')

## Packages
## General Packages
library(tidyverse)
# Formatting and Tables
library(kableExtra)
library(xtable)
# For plotting
library(ggplot2)
theme_set(theme_bw())
# Data manipulating
library(dplyr)
# ROC Analysis
library(pROC)

## One global parameter for printing figures
save.fig <- F

```


# Data Management

```{r data, tidy=T}

sim_results <- as_tibble(read.table('data/compiled_fit_results.txt', header=T,sep='\t'))

## Next, turn condition into a factor for plotting
sim_results$Condition <- as.factor(sim_results$Condition)

## Next, since TLI is non-normed, any value greater than 1 needs to be rescaled to 1.
sim_results$TLI <- ifelse(sim_results$TLI > 1, 1, sim_results$TLI)
sim_results$TLI <- ifelse(sim_results$TLI < 0, 0, sim_results$TLI)
## Next, summarize the results of the chi-square test of model fit. This is done simply by comparing the p-value to alpha (0.05) and indicating whether the model was flagged as fitting or not.
# Note: if  p < 0.05 then this variable is flagged as 0, and 1 otherwise
sim_results$Chi2_pvalue_decision <- ifelse(sim_results$chisqu_pvalue < 0.05, 0, 1)
# 0 = rejected that these data fit this model
# 1 = failed to reject that these data fit this model
```

## Adding Labels to Conditions

Currently, each condition is kind of like a hidden id that we don't know what the actual factor is. 
So, first thing isto create meaningful labels for us to use.
Remember, the 72 conditions for the this study were

  1. Level-1 sample size (5, 10, 30)
  2. Level-2 sample size (30, 50, 100, 200)
  3. Observed indicator ICC (.1, .3, .5)
  4. Latent variable ICC (.1, .5)
  
```{r}
## level-1 Sample size
ss_l1 <- c(5, 10, 30) ## 6 conditions each
ss_l2 <- c(30, 50, 100, 200) ## 18 condition each
icc_ov <- c(.1, .3, .5) ## 2 conditions each
icc_lv <- c(.1, .5) ## every other condition
nCon <- 72 # number of conditions
nRep <- 500 # number of replications per condition
nMod <- 12 ## numberof estimated models per conditions
## Total number of rows: 432,000
ss_l2 <- c(rep(ss_l2[1], 18*nRep*nMod), rep(ss_l2[2], 18*nRep*nMod), 
           rep(ss_l2[3], 18*nRep*nMod), rep(ss_l2[4], 18*nRep*nMod))
ss_l1 <- rep(c(rep(ss_l1[1],6*nRep*nMod), rep(ss_l1[2],6*nRep*nMod), rep(ss_l1[3],6*nRep*nMod)), 4)
icc_ov <- rep(c(rep(icc_ov[1], 2*nRep*nMod), rep(icc_ov[2], 2*nRep*nMod), rep(icc_ov[3], 2*nRep*nMod)), 12)
icc_lv <- rep(c(rep(icc_lv[1], nRep*nMod), rep(icc_lv[2], nRep*nMod)), 36)
## Force these vectors to be column vectors
ss_l1 <- matrix(ss_l1, ncol=1)
ss_l2 <- matrix(ss_l2, ncol=1)
icc_ov <- matrix(icc_ov, ncol=1)
icc_lv <- matrix(icc_lv, ncol=1)
## Add the labels to the results data frame
sim_results <- sim_results[order(sim_results$Condition),]
sim_results <- cbind(sim_results, ss_l1, ss_l2, icc_ov, icc_lv)

## Force the conditions to be factors
sim_results$ss_l1 <- as.factor(sim_results$ss_l1)
sim_results$ss_l2 <- as.factor(sim_results$ss_l2)
sim_results$icc_ov <- as.factor(sim_results$icc_ov)
sim_results$icc_lv <- as.factor(sim_results$icc_lv)
sim_results$Model <- factor(sim_results$Model, levels = c('C','M1','M2','M12'), ordered = T)
## Set up iterators for remainder of script
mods <- c('C', 'M1', 'M2', 'M12')
ests <- c('MLR', 'ULSMV', 'WLSMV')
```

# Descriptive Statistcs

For the descriptive statistics, I will use dplyr.
From here I can easily create matrices that store the results so that I can easily print out the results for summarizing the results.
Each will be printed out as a html table and a xtable (latex ready) table.

## Convergence Summary

Convergence will be broken out by Model (C, M1, M2, M12) and estimator (MLR, WLSMV, ULSMV). So, there will 12 tables piecemail tables and then one larger table.

```{r tb-con, tidy=T}

## first table summary table
c <- sim_results %>%
  group_by(Model, Estimator) %>%
  summarise(Converge=mean(Converge))
# Next make the columns the estimator factor
c <- cbind(c[ c$Estimator == 'MLR', 'Converge'], 
           c[ c$Estimator == 'ULSMV', 'Converge'], 
           c[ c$Estimator == 'WLSMV', 'Converge'])
colnames(c) <- c('MLR', 'ULSMV', 'WLSMV')
rownames(c) <- c('C' ,'M1' ,'M2', 'M12')
## Print results in a nice looking table in HTML
kable(c, format='html') %>%
    kable_styling(full_width = T)
## Print out in tex
print(xtable(c, digits = 3), booktabs = T, include.rownames = T)

# 
# ## Next, start the more descriptive tables across conditions
# ## loop around these iterators
# for(M in mods){
#   for(E in ests){
#     ### subset tothe model (M) and estimator (E)
#     #M <- 'C'
#     #E <- 'MLR'
#     cat('\n\n ===============================\n')
#     cat('\nModel:\t', M)
#     cat('\nEstimator:\t', E, '\n')
#     sub_dat <- sim_results[ sim_results$Model == M & sim_results$Estimator == E,]
#     
#     c <- sub_dat %>%
#         group_by(ss_l1, ss_l2, icc_ov, icc_lv) %>%
#         summarize(C = mean(Converge))
#     ## Now, print out the unformatted table
#       kable(c, format='html') %>%
#         kable_styling(full_width = T)
#       print(c)
#     ## now, make the columns the ICC conditions
#     c <- cbind(
#       c[ c$icc_ov == 0.1 & c$icc_lv == .1, c('ss_l1','ss_l2','C')], 
#       c[ c$icc_ov == 0.3 & c$icc_lv == .1, 'C'], 
#       c[ c$icc_ov == 0.5 & c$icc_lv == .1, 'C'], 
#       c[ c$icc_ov == 0.1 & c$icc_lv == .5, 'C'], 
#       c[ c$icc_ov == 0.3 & c$icc_lv == .5, 'C'], 
#       c[ c$icc_ov == 0.5 & c$icc_lv == .5, 'C']
#     ) ## End cbind()
#     colnames(c) <- c('ss_l1','ss_l2', '.1' ,'.3', '.5', '.1' ,'.3', '.5')
#     ## Print results in a nice looking table
#       kable(c, format='html') %>%
#         kable_styling(full_width = T) %>%
#         add_header_above(c(' ' = 2, 'LV ICC = .10' = 3, 'LV ICC = .50'=3))
#     
#     print(xtable(c, digits = 3), booktabs = T, include.rownames = F)
#   }
# }
# 
# 
# ## For a longtable instead
# c <-sim_results %>%
#       group_by(Model, Estimator, ss_l1, ss_l2, icc_ov, icc_lv) %>%
#       summarize(C = mean(Converge))
#     ## Now, print out the unformatted table
#       kable(c, format='html') %>%
#         kable_styling(full_width = T)
#       
#     ## now, make the columns the ICC conditions
#     c <- cbind(
#       c[ c$icc_ov == 0.1 & c$icc_lv == .1, c('Model', 'Estimator', 'ss_l1','ss_l2','C')], 
#       c[ c$icc_ov == 0.3 & c$icc_lv == .1, 'C'], 
#       c[ c$icc_ov == 0.5 & c$icc_lv == .1, 'C'], 
#       c[ c$icc_ov == 0.1 & c$icc_lv == .5, 'C'], 
#       c[ c$icc_ov == 0.3 & c$icc_lv == .5, 'C'], 
#       c[ c$icc_ov == 0.5 & c$icc_lv == .5, 'C']
#     ) ## End cbind()
#     colnames(c) <- c('Model', 'Estimator', 'ss_l1','ss_l2', '.1' ,'.3', '.5', '.1' ,'.3', '.5')
#     ## Print results in a nice looking table
#       kable(c, format='html') %>%
#         kable_styling(full_width = T) %>%
#         add_header_above(c(' ' = 4, 'LV ICC = .10' = 3, 'LV ICC = .50'=3))
#     
#     print(xtable(c, digits = 3), booktabs = T, include.rownames = F)

```

<!-- ## Admissibility Summary -->

<!-- Admissibility is checked in basically the exact same way. The only difference is that now I need to subset prior to making tables to models that converged. -->

<!-- ```{r tb-admiss, tidy=T} -->
<!-- ## Subset fo converged -->
<!-- con_results <- filter(sim_results, Converge == 1) -->

<!-- ## first table summary table -->
<!-- a <- con_results %>% -->
<!--   group_by(Model, Estimator) %>% -->
<!--   summarise(A=mean(Admissible)) -->
<!-- # Next make the columns the estimator factor -->
<!-- a <- cbind(a[ a$Estimator == 'MLR', 'A'],  -->
<!--            a[ a$Estimator == 'ULSMV', 'A'],  -->
<!--            a[ a$Estimator == 'WLSMV', 'A']) -->
<!-- colnames(a) <- c('MLR', 'ULSMV', 'WLSMV') -->
<!-- rownames(a) <- c('C' ,'M1' ,'M2', 'M12') -->
<!-- ## Print results in a nice looking table in HTML -->
<!-- kable(a, format='html') %>% -->
<!--     kable_styling(full_width = T) -->
<!-- ## Print out in tex -->
<!-- print(xtable(a, digits = 3), booktabs = T, include.rownames = T) -->


<!-- ## Next, start the more descriptive tables across conditions -->
<!-- ## loop around these iterators -->
<!-- for(M in mods){ -->
<!--   for(E in ests){ -->
<!--     ### subset tothe model (M) and estimator (E) -->
<!--     #M <- 'C' -->
<!--     #E <- 'MLR' -->
<!--     cat('\n\n ===============================\n') -->
<!--     cat('\nModel:\t', M) -->
<!--     cat('\nEstimator:\t', E, '\n') -->
<!--     sub_dat <- con_results[ con_results$Model == M & con_results$Estimator == E,] -->

<!--     a <- sub_dat %>% -->
<!--         group_by(ss_l1, ss_l2, icc_ov, icc_lv) %>% -->
<!--         summarize(C = mean(Admissible)) -->
<!--     ## Now, print out the unformatted table -->
<!--     kable(a, format='html') %>% -->
<!--         kable_styling(full_width = T) -->
<!--     print(a) -->

<!--     ## now, make the columns the ICC conditions -->
<!--     a <- cbind( -->
<!--       a[ a$icc_ov == 0.1 & a$icc_lv == .1, c('ss_l1','ss_l2','C')],  -->
<!--       a[ a$icc_ov == 0.3 & a$icc_lv == .1, 'C'],  -->
<!--       a[ a$icc_ov == 0.5 & a$icc_lv == .1, 'C'],  -->
<!--       a[ a$icc_ov == 0.1 & a$icc_lv == .5, 'C'],  -->
<!--       a[ a$icc_ov == 0.3 & a$icc_lv == .5, 'C'],  -->
<!--       a[ a$icc_ov == 0.5 & a$icc_lv == .5, 'C'] -->
<!--     ) ## End cbind() -->
<!--     colnames(a) <- c('ss_l1','ss_l2', '.1' ,'.3', '.5', '.1' ,'.3', '.5') -->
<!--     ## Print results in a nice looking table -->
<!--     kable(a, format='html') %>% -->
<!--         kable_styling(full_width = T) %>% -->
<!--         add_header_above(c(' ' = 2, 'LV ICC = .10' = 3, 'LV ICC = .50'=3)) -->

<!--     print(xtable(a, digits = 3), booktabs = T, include.rownames = F) -->
<!--   } -->
<!-- } -->


<!-- ## For a longtable.. -->
<!-- c <-con_results %>% -->
<!--       group_by(Model, Estimator, ss_l1, ss_l2, icc_ov, icc_lv) %>% -->
<!--       summarize(C = mean(Admissible)) -->
<!--     ## Now, print out the unformatted table -->
<!--       kable(c, format='html') %>% -->
<!--         kable_styling(full_width = T) -->

<!--     ## now, make the columns the ICC conditions -->
<!--     c <- cbind( -->
<!--       c[ c$icc_ov == 0.1 & c$icc_lv == .1, c('Model', 'Estimator', 'ss_l1','ss_l2','C')],  -->
<!--       c[ c$icc_ov == 0.3 & c$icc_lv == .1, 'C'],  -->
<!--       c[ c$icc_ov == 0.5 & c$icc_lv == .1, 'C'],  -->
<!--       c[ c$icc_ov == 0.1 & c$icc_lv == .5, 'C'],  -->
<!--       c[ c$icc_ov == 0.3 & c$icc_lv == .5, 'C'],  -->
<!--       c[ c$icc_ov == 0.5 & c$icc_lv == .5, 'C'] -->
<!--     ) ## End cbind() -->
<!--     colnames(c) <- c('Model', 'Estimator', 'ss_l1','ss_l2', '.1' ,'.3', '.5', '.1' ,'.3', '.5') -->
<!--     ## Print results in a nice looking table -->
<!--       kable(c, format='html') %>% -->
<!--         kable_styling(full_width = T) %>% -->
<!--         add_header_above(c(' ' = 4, 'LV ICC = .10' = 3, 'LV ICC = .50'=3)) -->

<!--     print(xtable(c, digits = 3), booktabs = T, include.rownames = F) -->
<!-- ``` -->


<!-- Make figure for the defense of the converged and admissible summary. -->

<!-- ```{r} -->

<!-- c <- sim_results %>% -->
<!--   group_by(Model, Estimator) %>% -->
<!--   summarise(Converge=mean(Converge)) -->

<!-- ## Subset fo converged -->
<!-- con_results <- filter(sim_results, Converge == 1) -->

<!-- ## first table summary table -->
<!-- a <- con_results %>% -->
<!--   group_by(Model, Estimator) %>% -->
<!--   summarise(A=mean(Admissible)) -->

<!-- c$c <- rep('Converge', 12) -->
<!-- a$a <- rep('Admissible', 12) -->
<!-- colnames(c) <- colnames(a) <- c('Model', 'Estimator', 'Prop', 'Type') -->

<!-- ca_dat <- rbind(c, a) -->
<!-- ca_dat$Type <- as.factor(ca_dat$Type) -->
<!-- ca_dat -->

<!-- # Figure -------------------- -->

<!-- ggplot(ca_dat, aes(x = Model, y = Prop, color = Type, group = Estimator)) + -->
<!--   geom_line() -->

<!-- ``` -->



<!-- ## Descriptive Statistics of Fit Indices -->

<!-- Now for the long process of making tables for the MANY conditions for the descriptive statistics. -->
<!-- For this, we need to do this is steps so that all the information gets outputted in the correct manor for table.  -->
<!-- For each statistic under each condition, model, and estimator, the code below create a table that contains the average value and the standard deviation. -->
<!-- Again, just like the descriptives above, a summary table was made to start. -->

<!-- These tables are made based only on the 1) converged models and 2) the admissible solutions. -->

<!-- The fit indices included are: -->

<!--   1. Chi-square p-value summary, i.e. proportion of tims the p-value was greater than 0.05. No SD is reported here. -->
<!--   2. CFI with mean and sd -->
<!--   3. TLI with mean and sd -->
<!--   4. RMSEA with mean and sd -->
<!--   5. SRMRW with mean and sd -->
<!--   6. SRMRB with mean and sd -->

<!-- ```{r fit-sum} -->

<!-- mydata <- filter(sim_results, Converge == 1 & Admissible == 1) -->

<!-- ## first table summary table -->
<!-- a <- mydata %>% -->
<!--   group_by(Model, Estimator) %>% -->
<!--   summarise( -->
<!--     chi2=mean(Chi2_pvalue_decision, na.rm = T), -->
<!--     CFI.m =mean(CFI, na.rm = T), CFI.sd =sd(CFI, na.rm = T), -->
<!--     TLI.m =mean(TLI, na.rm = T), TLI.sd =sd(TLI, na.rm = T), -->
<!--     RMSEA.m =mean(RMSEA, na.rm = T), RMSEA.sd =sd(RMSEA, na.rm = T), -->
<!--     SRMRW.m =mean(SRMRW, na.rm = T), SRMRW.sd =sd(SRMRW, na.rm = T), -->
<!--     SRMRB.m =mean(SRMRB, na.rm = T), SRMRB.sd =sd(SRMRB, na.rm = T) -->
<!--   ) -->
<!-- ## Print results in a nice looking table in HTML -->
<!-- kable(a, format='html') %>% -->
<!--     kable_styling(full_width = T) -->

<!-- ## make a copy of a to print into -->
<!-- a1 <- as_tibble(as.data.frame(matrix(NA, ncol=8,nrow=nrow(a)))) -->
<!-- colnames(a1) <- c('Model', 'Estimator', "chi2", "CFI",'TLI', 'RMSEA', 'SRMRW', 'SRMRB') -->
<!-- i <- 1 -->
<!-- for(i in 1:nrow(a)){ -->
<!--   a1[i,3:8] <- unlist(c( -->
<!--     round(a[i,3],3),  -->
<!--   paste0(round(a[i,4],3), ' (', round(a[i,5],2), ')'), -->
<!--   paste0(round(a[i,6],3), ' (', round(a[i,7],2), ')'), -->
<!--   paste0(round(a[i,8],3), ' (', round(a[i,9],2), ')'), -->
<!--   paste0(round(a[i,10],3), ' (', round(a[i,11],2), ')'), -->
<!--   paste0(round(a[i,12],3), ' (', round(a[i,12],2), ')') -->
<!--   )) -->
<!-- } -->
<!-- a1[,1:2] <- a[,1:2]## add factors back -->
<!-- ## Print out in tex -->
<!-- print(xtable(a1, digits = 3), booktabs = T, include.rownames = F) -->

<!-- ## Now, create MANY subset tables to breakdown these relationships -->
<!-- ## loop around these iterators -->
<!-- for(M in mods){ -->
<!--   for(E in ests){ -->
<!--     ### subset tothe model (M) and estimator (E) -->
<!--     #M <- 'C' -->
<!--     #E <- 'MLR' -->
<!--     cat('\n\n ===============================\n') -->
<!--     cat('\nModel:\t', M) -->
<!--     cat('\nEstimator:\t', E, '\n') -->
<!--     sub_dat <- mydata[ mydata$Model == M & mydata$Estimator == E,] -->

<!--     a <- sub_dat %>% -->
<!--         group_by(ss_l1, ss_l2, icc_ov, icc_lv) %>% -->
<!--         summarise( -->
<!--           chi2=mean(Chi2_pvalue_decision, na.rm = T), -->
<!--           CFI.m =mean(CFI, na.rm = T), CFI.sd =sd(CFI, na.rm = T), -->
<!--           TLI.m =mean(TLI, na.rm = T), TLI.sd =sd(TLI, na.rm = T), -->
<!--           RMSEA.m =mean(RMSEA, na.rm = T), RMSEA.sd =sd(RMSEA, na.rm = T), -->
<!--           SRMRW.m =mean(SRMRW, na.rm = T), SRMRW.sd =sd(SRMRW, na.rm = T), -->
<!--           SRMRB.m =mean(SRMRB, na.rm = T), SRMRB.sd =sd(SRMRB, na.rm = T) -->
<!--         ) -->
<!--     ## Print results in a nice looking table -->
<!--     kable(a, format='html') %>% -->
<!--         kable_styling(full_width = T) -->

<!--     ## Now, create subsets of this results matrix for outputting into small(ish) tables -->
<!--     ## Subset by ICC conditions -->
<!--     ICCO <- unique(a$icc_ov) -->
<!--     ICCL <- unique(a$icc_lv) -->
<!--     icco <- ICCO[1] -->
<!--     iccl <- ICCL[1] -->
<!--     for(icco in ICCO){ -->
<!--       for(iccl in ICCL){ -->
<!--         ### subset tothe model (M) and estimator (E) -->
<!--         #M <- 'C' -->
<!--         #E <- 'MLR' -->
<!--         cat('\n\n ===============================\n') -->
<!--         cat('\nModel:\t', M) -->
<!--         cat('\nEstimator:\t', E) -->
<!--         cat('\nICC Obs. Var.:\t', icco) -->
<!--         cat('\nICC Lat. Var.:\t', iccl,'\n') -->
<!--         a_s <- filter(a, icc_ov == icco, icc_lv == iccl) -->
<!--         ## make a copy of a to print into -->
<!--         a1 <- as_tibble(as.data.frame(matrix(NA, ncol=8,nrow=nrow(a_s)))) -->
<!--         colnames(a1) <- c('N2', 'N1', "chi2", "CFI",'TLI', 'RMSEA', 'SRMRW', 'SRMRB') -->
<!--         i <- 1 -->
<!--         for(i in 1:nrow(a_s)){ -->
<!--           a1[i,3:8] <- unlist(c( -->
<!--             round(a_s[i,5],2),  -->
<!--           paste0(round(a_s[i,6],2), '(', round(a_s[i,7],2), ')'), -->
<!--           paste0(round(a_s[i,8],2), '(', round(a_s[i,9],2), ')'), -->
<!--           paste0(round(a_s[i,10],2), '(', round(a_s[i,11],2), ')'), -->
<!--           paste0(round(a_s[i,12],2), '(', round(a_s[i,13],2), ')'), -->
<!--           paste0(round(a_s[i,14],2), '(', round(a_s[i,15],2), ')') -->
<!--           )) -->
<!--         } -->
<!--         a1[,1:2] <- a_s[,c(2,1)]## add factors back with diff. order -->
<!--         ## Print out in tex -->
<!--         print(xtable(a1, -->
<!--                      caption = paste0('Summary of Fit Statistics Across Conditions: Model ',M,', Estimator ',E,', ICC_O ',icco,' and ICC_L ', iccl)), booktabs = T, include.rownames = F) -->
<!--       } -->
<!--     }## End subset table printing -->
<!--   } -->
<!-- } ## End loops.. -->

<!-- ``` -->

<!-- # Boxplots -->

<!-- One of the best ways to visualize the results of the distribution of fit statistics across conditions is to use boxplots. -->
<!-- In the section, I create three sets of boxplots. -->
<!-- First, the boxplots are large and give a very course overview of  the results across conditions, but can be difficult to make sense of because of how large they are. -->
<!-- Secondly, the boxplots are made with facets by model and estimator from the larger set of data so that more concise plots can be made for easier viewing. -->
<!-- Third, subsets based on Model and estimator are made to create a "smaller" plot that is easier to handle. -->
<!-- Most of these latter plots are  included in my thesis document. -->

<!-- For all graphs, I haved placed a dashed line where the commonly used cut-off for these fit statistics lies. -->


<!-- ```{r box-dat} -->

<!-- mydata <- filter(sim_results, Converge == 1 & Admissible == 1) -->

<!-- ``` -->


<!-- ## Large General Boxplots -->

<!-- For these larger Boxplots, there are two sets. -->

<!--   1. Coarse distributions of each fit statistic -->

<!--   2. Marginal Plots of Condition (ss\_l1, ss\_l2, icc\_ov, icc\_lv) -->

<!-- ### Coarse Boxplots  -->

<!-- ```{r gen-box-1} -->

<!-- ## Set 1 Coarse distributions of each fit statistic -->
<!-- p <- ggplot(mydata, aes(x=Condition, y=CFI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0,  -->
<!--                 linetype='dashed', color = 'red') -->
<!-- p -->
<!-- if(save.fig == T) ggsave("cfi_all_conditions.pdf",plot = p, width=12, height=6, units='in') -->

<!-- p <- ggplot(mydata, aes(x=Condition, y=TLI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0,  -->
<!--                 linetype='dashed', color = 'red')  -->
<!-- p -->
<!-- if(save.fig == T) ggsave("tli_all_conditions.pdf",plot = p, width=12, height=6, units='in') -->

<!-- p <- ggplot(mydata, aes(x=Condition, y=RMSEA))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .06, slope=0,  -->
<!--                 linetype='dashed', color = 'red')  -->
<!-- p -->
<!-- if(save.fig == T) ggsave("rmsea_all_conditions.pdf",plot = p, width=12, height=6, units='in') -->

<!-- p <- ggplot(mydata, aes(x=Condition, y=SRMRW))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0,  -->
<!--                 linetype='dashed', color = 'red')  -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrw_all_conditions.pdf",plot = p, width=12, height=6, units='in') -->

<!-- p <- ggplot(mydata, aes(x=Condition, y=SRMRB))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0,  -->
<!--                 linetype='dashed', color = 'red')  -->
<!--     lims(y=c(0,1)) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrb_all_conditions.pdf",plot = p, width=12, height=6, units='in') -->

<!-- ``` -->

<!-- ### Marginal Plots of Conditions -->

<!-- #### CFI -->

<!-- ```{r gen-box-cfi} -->
<!-- p <- ggplot(mydata, aes(x=Model, y=CFI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red')  -->
<!-- p -->
<!-- if(save.fig == T) ggsave("cfi_marginal_model.pdf",plot = p, width=6, height=4, units='in') -->

<!-- p <- ggplot(mydata, aes(x=Estimator, y=CFI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') -->
<!-- p -->
<!-- if(save.fig == T) ggsave("cfi_marginal_estimator.pdf",plot = p, width=6, height=4, units='in') -->

<!-- p <- ggplot(mydata, aes(x=ss_l1, y=CFI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red')  -->
<!-- p -->
<!-- if(save.fig == T) ggsave("cfi_marginal_ssl1.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=ss_l2, y=CFI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red')  -->
<!-- p -->
<!-- if(save.fig == T) ggsave("cfi_marginal_ss_l2.pdf",plot = p,width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=icc_ov, y=CFI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     labs(title = 'CFI by Obs. Var. ICC') -->
<!-- p -->
<!-- if(save.fig == T) ggsave("cfi_marginal_icc_ov.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=icc_lv, y=CFI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red')  -->
<!-- p -->
<!-- if(save.fig == T) ggsave("cfi_marginal_icc_lv.pdf",plot = p, width=6, height=4, units='in') -->


<!-- ``` -->

<!-- #### TLI -->

<!-- ```{r gen-box-tli} -->
<!-- p <- ggplot(mydata, aes(x=Model, y=TLI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') -->
<!-- p -->
<!-- if(save.fig == T) ggsave("tli_marginal_model.pdf",plot = p, width=6, height=4, units='in') -->
<!-- p <- ggplot(mydata, aes(x=Estimator, y=TLI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') -->
<!-- p -->
<!-- if(save.fig == T) ggsave("tli_marginal_estimator.pdf",plot = p,width=6, height=4, units='in') -->

<!-- p <- ggplot(mydata, aes(x=ss_l1, y=TLI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red')  -->
<!-- p -->
<!-- if(save.fig == T) ggsave("tli_marginal_ss_l1.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=ss_l2, y=TLI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') -->
<!-- p -->
<!-- if(save.fig == T) ggsave("tli_marginal_ss_l2.pdf",plot = p, width=6, height=4, units='in') -->

<!-- p <- ggplot(mydata, aes(x=icc_ov, y=TLI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') -->
<!-- p -->
<!-- if(save.fig == T) ggsave("tli_marginal_icc_ov.pdf",plot = p, width=6, height=4, units='in') -->

<!-- p <- ggplot(mydata, aes(x=icc_lv, y=TLI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red')  -->
<!-- p -->
<!-- if(save.fig == T) ggsave("tli_marginal_icc_lv.pdf",plot = p, width=6, height=4, units='in') -->


<!-- ``` -->

<!-- #### RMSEA -->

<!-- ```{r gen-box-rmsea} -->
<!-- p <- ggplot(mydata, aes(x=Model, y=RMSEA))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .06, slope=0, -->
<!--                 linetype='dashed', color = 'red')  -->
<!-- p -->
<!-- if(save.fig == T) ggsave("rmsea_marginal_model.pdf",plot = p, width=6, height=4, units='in') -->

<!-- p <- ggplot(mydata, aes(x=Estimator, y=RMSEA))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .06, slope=0, -->
<!--                 linetype='dashed', color = 'red') -->
<!-- p -->
<!-- if(save.fig == T) ggsave("rmsea_marginal_estimator.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=ss_l1, y=RMSEA))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .06, slope=0, -->
<!--                 linetype='dashed', color = 'red') -->
<!-- p -->
<!-- if(save.fig == T) ggsave("rmsea_marginal_ss_l1.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=ss_l2, y=RMSEA))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .06, slope=0, -->
<!--                 linetype='dashed', color = 'red')  -->
<!-- p -->
<!-- if(save.fig == T) ggsave("rmsea_marginal_ss_l2.pdf",plot = p, width=6, height=4, units='in') -->

<!-- p <- ggplot(mydata, aes(x=icc_ov, y=RMSEA))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .06, slope=0, -->
<!--                 linetype='dashed', color = 'red') -->
<!-- p -->
<!-- if(save.fig == T) ggsave("rmsea_marginal_icc_ov.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=icc_lv, y=RMSEA))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .06, slope=0, -->
<!--                 linetype='dashed', color = 'red') -->
<!-- p -->
<!-- if(save.fig == T) ggsave("rmsea_marginal_icc_lv.pdf",plot = p, width=6, height=4, units='in') -->


<!-- ``` -->

<!-- #### SRMRW -->

<!-- ```{r gen-box-srmrw} -->

<!-- p <- ggplot(mydata, aes(x=Model, y=SRMRW))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red')  -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrw_marginal_model.pdf",plot = p, width=6, height=4, units='in') -->

<!-- p <- ggplot(mydata, aes(x=Estimator, y=SRMRW))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrw_marginal_estimator.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=ss_l1, y=SRMRW))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red')  -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrw_marginal_ss_l1.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=ss_l2,  y=SRMRW))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrw_marginal_ss_l2.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=icc_ov,  y=SRMRW))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     labs(title = 'SRMRW by Obs. Var. ICC') -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrw_marginal_icc_ov.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=icc_lv, y=SRMRW))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrw_marginal_icc_lv.pdf",plot = p, width=6, height=4, units='in') -->

<!-- ``` -->

<!-- #### SRMRB -->

<!-- ```{r gen-box-srmrb} -->

<!-- p <- ggplot(mydata, aes(x=Model, y=SRMRB))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red')+ -->
<!--     lims(y=c(0,1))  -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrb_marginal_model.pdf",plot = p, width=6, height=4, units='in') -->

<!-- p <- ggplot(mydata, aes(x=Estimator, y=SRMRB))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red')+ -->
<!--     lims(y=c(0,1))  -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrb_marginal_estimator.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=ss_l1, y=SRMRB))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     lims(y=c(0,1))  -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrb_marginal_ss_l1.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=ss_l2,  y=SRMRB))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     labs(title = 'SRMRB by Level-2 Sample Size') + -->
<!--     lims(y=c(0,1)) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrb_marginal_ss_l2.pdf",plot = p, width=6, height=4, units='in') -->

<!-- p <- ggplot(mydata, aes(x=icc_ov,  y=SRMRB))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     lims(y=c(0,1)) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrb_marginal_icc_ov.pdf",plot = p, width=6, height=4, units='in') -->

<!-- p <- ggplot(mydata, aes(x=icc_lv, y=SRMRB))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     lims(y=c(0,1)) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrb_marginal_icc_lv.pdf",plot = p, width=6, height=4, units='in') -->

<!-- ``` -->

<!-- ## Facetted Boxplots -->

<!-- For the facetted boxplots, these will also be created in multiple sets. -->

<!--   1. Full Results by conditions faetted by Model and estimator -->
<!--   2.  Marginal Plots of Condition (ss\_l1, ss\_l2, icc\_ov, icc\_lv) Facetted by Est. -->
<!--   3.  Marginal Plots of Condition (ss\_l1, ss\_l2, icc\_ov, icc\_lv) Facetted by Model -->
<!--   4.  Marginal Plots of Condition (ss\_l1, ss\_l2, icc\_ov, icc\_lv) Facetted by Est. and Model -->

<!-- So, that is a lot of plots and onyl a select few will make it into the final document and publication manuscript. -->

<!-- ### Faceted Coarse Boxplots -->

<!-- ```{r fac-box-1} -->
<!-- ## Set 1: Large boxplot figures faceted by Model and Estimator -->
<!-- p <- ggplot(mydata, aes(x=Condition, y=CFI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(Model~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("cfi_all_condition_facet.pdf",plot = p, width=16, height=12, units='in') -->

<!-- p <- ggplot(mydata, aes(x=Condition, y=TLI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(Model~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("tli_all_condition_facet.pdf",plot = p, width=16, height=12, units='in') -->

<!-- p <- ggplot(mydata, aes(x=Condition, y=RMSEA))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .06, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(Model~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("rmsea_all_condition_facet.pdf",plot = p, width=16, height=12, units='in') -->


<!-- p <- ggplot(mydata, aes(x=Condition, y=SRMRW))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(Model~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrw_all_condition_facet.pdf",plot = p, width=16, height=12, units='in') -->

<!-- p <- ggplot(mydata, aes(x=Condition, y=SRMRB))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(Model~Estimator) + -->
<!--     lims(y=c(0,1)) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrb_all_condition_facet.pdf",plot = p, width=16, height=12, units='in') -->
<!-- ``` -->


<!-- ### Marginal Plots of Conditions Facetted by Estimator -->

<!-- #### CFI -->

<!-- ```{r fac-e-box-cfi} -->

<!-- p <- ggplot(mydata, aes(x=ss_l1, y=CFI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("cfi_marginal_ssl1_facet_estimator.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=ss_l2, y=CFI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Estimator)+ -->
<!--     labs(title = 'CFI by Level-2 Sample Size') -->
<!-- p -->
<!-- if(save.fig == T) ggsave("cfi_marginal_ss_l2_facet_estimator.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=icc_ov, y=CFI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("cfi_marginal_icc_ov_facet_estimator.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=icc_lv, y=CFI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("cfi_marginal_icc_lv_facet_estimator.pdf",plot = p, width=6, height=4, units='in') -->


<!-- ``` -->

<!-- #### TLI -->

<!-- ```{r fac-e-box-tli} -->

<!-- p <- ggplot(mydata, aes(x=ss_l1, y=TLI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("tli_marginal_ss_l1_facet_estimator.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=ss_l2, y=TLI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("tli_marginal_ss_l2_facet_estimator.pdf",plot = p, width=6, height=4, units='in') -->

<!-- p <- ggplot(mydata, aes(x=icc_ov, y=TLI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("tli_marginal_icc_ov_facet_estimator.pdf",plot = p, scale=1) -->

<!-- p <- ggplot(mydata, aes(x=icc_lv, y=TLI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("tli_marginal_icc_lv_facet_estimator.pdf",plot = p, width=6, height=4, units='in') -->


<!-- ``` -->

<!-- #### RMSEA -->

<!-- ```{r fac-e-box-rmsea} -->

<!-- p <- ggplot(mydata, aes(x=ss_l1, y=RMSEA))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .06, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("rmsea_marginal_ss_l1_facet_estimator.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=ss_l2, y=RMSEA))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .06, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("rmsea_marginal_ss_l2_facet_estimator.pdf",plot = p, width=6, height=4, units='in') -->

<!-- p <- ggplot(mydata, aes(x=icc_ov, y=RMSEA))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .06, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("rmsea_marginal_icc_ov_facet_estimator.pdf",plot = p,width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=icc_lv, y=RMSEA))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .06, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("rmsea_marginal_icc_lv_facet_estimator.pdf",plot = p, width=6, height=4, units='in') -->


<!-- ``` -->

<!-- #### SRMRW -->

<!-- ```{r fac-e-box-srmrw} -->

<!-- p <- ggplot(mydata, aes(x=ss_l1, y=SRMRW))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrw_marginal_ss_l1_facet_estimator.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=ss_l2,  y=SRMRW))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrw_marginal_ss_l2_facet_estimator.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=icc_ov,  y=SRMRW))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrw_marginal_icc_ov_facet_estimator.pdf",plot = p,width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=icc_lv, y=SRMRW))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrw_marginal_icc_lv_facet_estimator.pdf",plot = p, width=6, height=4, units='in') -->

<!-- ``` -->

<!-- #### SRMRB -->

<!-- ```{r fac-e-box-srmrb} -->

<!-- p <- ggplot(mydata, aes(x=ss_l1, y=SRMRB))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Estimator) + -->
<!--     lims(y=c(0,1)) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrb_marginal_ss_l1_facet_estimator.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=ss_l2,  y=SRMRB))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Estimator) + -->
<!--     lims(y=c(0,1)) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrb_marginal_ss_l2_facet_estimator.pdf",plot = p, width=6, height=4, units='in') -->

<!-- p <- ggplot(mydata, aes(x=icc_ov,  y=SRMRB))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Estimator)+ -->
<!--     lims(y=c(0,1)) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrb_marginal_icc_ov_facet_estimator.pdf",plot = p, width=6, height=4, units='in') -->

<!-- p <- ggplot(mydata, aes(x=icc_lv, y=SRMRB))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Estimator)+ -->
<!--     lims(y=c(0,1)) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrb_marginal_icc_lv_facet_estimator.pdf",plot = p, width=6, height=4, units='in') -->

<!-- ``` -->


<!-- ### Marginal Plots of Conditions Facetted by Model -->

<!-- #### CFI -->

<!-- ```{r fac-m-box-cfi} -->

<!-- p <- ggplot(mydata, aes(x=ss_l1, y=CFI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Model) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("cfi_marginal_ssl1_facet_model.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=ss_l2, y=CFI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Model) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("cfi_marginal_ss_l2_facet_model.pdf",plot = p,width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=icc_ov, y=CFI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Model) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("cfi_marginal_icc_ov_facet_model.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=icc_lv, y=CFI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Model) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("cfi_marginal_icc_lv_facet_model.pdf",plot = p, width=6, height=4, units='in') -->


<!-- ``` -->

<!-- #### TLI -->

<!-- ```{r fac-m-box-tli} -->

<!-- p <- ggplot(mydata, aes(x=ss_l1, y=TLI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Model) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("tli_marginal_ss_l1_facet_model.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=ss_l2, y=TLI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Model)+ -->
<!--     labs(title = 'TLI by Level-2 Sample Size') -->
<!-- p -->
<!-- if(save.fig == T) ggsave("tli_marginal_ss_l2_facet_model.pdf",plot = p, width=6, height=4, units='in') -->

<!-- p <- ggplot(mydata, aes(x=icc_ov, y=TLI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Model) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("tli_marginal_icc_ov_facet_model.pdf",plot = p, width=6, height=4, units='in') -->

<!-- p <- ggplot(mydata, aes(x=icc_lv, y=TLI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Model) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("tli_marginal_icc_lv_facet_model.pdf",plot = p, width=6, height=4, units='in') -->


<!-- ``` -->

<!-- #### RMSEA -->

<!-- ```{r fac-m-box-rmsea} -->

<!-- p <- ggplot(mydata, aes(x=ss_l1, y=RMSEA))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .06, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Model) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("rmsea_marginal_ss_l1_facet_model.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=ss_l2, y=RMSEA))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .06, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Model) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("rmsea_marginal_ss_l2_facet_model.pdf",plot = p, width=6, height=4, units='in') -->

<!-- p <- ggplot(mydata, aes(x=icc_ov, y=RMSEA))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .06, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Model) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("rmsea_marginal_icc_ov_facet_model.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=icc_lv, y=RMSEA))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .06, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Model) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("rmsea_marginal_icc_lv_facet_model.pdf",plot = p, width=6, height=4, units='in') -->


<!-- ``` -->

<!-- #### SRMRW -->

<!-- ```{r fac-m-box-srmrw} -->

<!-- p <- ggplot(mydata, aes(x=ss_l1, y=SRMRW))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Model) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrw_marginal_ss_l1_facet_model.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=ss_l2,  y=SRMRW))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Model) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrw_marginal_ss_l2_facet_model.pdf",plot = p, scale=1) -->


<!-- p <- ggplot(mydata, aes(x=icc_ov,  y=SRMRW))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Model) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrw_marginal_icc_ov_facet_model.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=icc_lv, y=SRMRW))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Model) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrw_marginal_icc_lv_facet_model.pdf",plot = p, width=6, height=4, units='in') -->

<!-- ``` -->

<!-- #### SRMRB -->

<!-- ```{r fac-m-box-srmrb} -->

<!-- p <- ggplot(mydata, aes(x=ss_l1, y=SRMRB))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Model)+ -->
<!--     lims(y=c(0,1)) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrb_marginal_ss_l1_facet_model.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=ss_l2,  y=SRMRB))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Model)+ -->
<!--     lims(y=c(0,1)) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrb_marginal_ss_l2_facet_model.pdf",plot = p, width=6, height=4, units='in') -->

<!-- p <- ggplot(mydata, aes(x=icc_ov,  y=SRMRB))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Model)+ -->
<!--     lims(y=c(0,1)) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrb_marginal_icc_ov_facet_model.pdf",plot = p, width=6, height=4, units='in') -->

<!-- p <- ggplot(mydata, aes(x=icc_lv, y=SRMRB))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(.~Model)+ -->
<!--     lims(y=c(0,1)) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrb_marginal_icc_lv_facet_model.pdf",plot = p, width=6, height=4, units='in') -->

<!-- ``` -->


<!-- ### Marginal Plots of Conditions Facetted by Estimator and Model -->

<!-- #### CFI -->

<!-- ```{r fac-em-box-cfi} -->

<!-- p <- ggplot(mydata, aes(x=ss_l1, y=CFI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(Model~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("cfi_marginal_ssl1_facet_estimator_model.pdf",plot = p, width=9, height=6, units='in') -->


<!-- p <- ggplot(mydata, aes(x=ss_l2, y=CFI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(Model~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("cfi_marginal_ss_l2_facet_estimator_model.pdf",plot = p, width=9, height=6, units='in') -->


<!-- p <- ggplot(mydata, aes(x=icc_ov, y=CFI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(Model~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("cfi_marginal_icc_ov_facet_estimator_model.pdf",plot = p, width=9, height=6, units='in') -->


<!-- p <- ggplot(mydata, aes(x=icc_lv, y=CFI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(Model~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("cfi_marginal_icc_lv_facet_estimator_model.pdf",plot = p, width=9, height=6, units='in') -->


<!-- ``` -->

<!-- #### TLI -->

<!-- ```{r fac-em-box-tli} -->

<!-- p <- ggplot(mydata, aes(x=ss_l1, y=TLI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(Model~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("tli_marginal_ss_l1_facet_estimator_model.pdf",plot = p, width=9, height=6, units='in') -->


<!-- p <- ggplot(mydata, aes(x=ss_l2, y=TLI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(Model~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("tli_marginal_ss_l2_facet_estimator_model.pdf",plot = p, width=9, height=6, units='in') -->

<!-- p <- ggplot(mydata, aes(x=icc_ov, y=TLI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(Model~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("tli_marginal_icc_ov_facet_estimator_model.pdf",plot = p, width=9, height=6, units='in') -->

<!-- p <- ggplot(mydata, aes(x=icc_lv, y=TLI))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(Model~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("tli_marginal_icc_lv_facet_estimator_model.pdf",plot = p, width=9, height=6, units='in') -->


<!-- ``` -->

<!-- #### RMSEA -->

<!-- ```{r fac-em-box-rmsea} -->

<!-- p <- ggplot(mydata, aes(x=ss_l1, y=RMSEA))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .06, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(Model~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("rmsea_marginal_ss_l1_facet_estimator_model.pdf",plot = p, width=9, height=6, units='in') -->


<!-- p <- ggplot(mydata, aes(x=ss_l2, y=RMSEA))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .06, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(Model~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("rmsea_marginal_ss_l2_facet_estimator_model.pdf",plot = p, width=9, height=6, units='in') -->

<!-- p <- ggplot(mydata, aes(x=icc_ov, y=RMSEA))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .06, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(Model~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("rmsea_marginal_icc_ov_facet_estimator_model.pdf",plot = p, width=9, height=6, units='in') -->


<!-- p <- ggplot(mydata, aes(x=icc_lv, y=RMSEA))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .06, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(Model~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("rmsea_marginal_icc_lv_facet_estimator_model.pdf",plot = p, width=9, height=6, units='in') -->


<!-- ``` -->

<!-- #### SRMRW -->

<!-- ```{r fac-em-box-srmrw} -->

<!-- p <- ggplot(mydata, aes(x=ss_l1, y=SRMRW))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(Model~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrw_marginal_ss_l1_facet_estimator_model.pdf",plot = p, width=9, height=6, units='in') -->


<!-- p <- ggplot(mydata, aes(x=ss_l2,  y=SRMRW))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(Model~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrw_marginal_ss_l2_facet_estimator_model.pdf",plot = p, width=9, height=6, units='in') -->


<!-- p <- ggplot(mydata, aes(x=icc_ov,  y=SRMRW))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(Model~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrw_marginal_icc_ov_facet_estimator_model.pdf",plot = p, width=9, height=6, units='in') -->


<!-- p <- ggplot(mydata, aes(x=icc_lv, y=SRMRW))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(Model~Estimator) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrw_marginal_icc_lv_facet_estimator_model.pdf",plot = p, width=9, height=6, units='in') -->

<!-- ``` -->

<!-- #### SRMRB -->

<!-- ```{r fac-em-box-srmrb} -->

<!-- p <- ggplot(mydata, aes(x=ss_l1, y=SRMRB))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(Model~Estimator)+ -->
<!--     lims(y=c(0,1)) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrb_marginal_ss_l1_facet_estimator_model.pdf",plot = p, width=9, height=6, units='in') -->


<!-- p <- ggplot(mydata, aes(x=ss_l2,  y=SRMRB))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(Model~Estimator)+ -->
<!--     lims(y=c(0,1)) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrb_marginal_ss_l2_facet_estimator_model.pdf",plot = p, width=9, height=6, units='in') -->

<!-- p <- ggplot(mydata, aes(x=icc_ov,  y=SRMRB))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(Model~Estimator)+ -->
<!--     labs(title = 'SRMRB by Obs. Var. ICC')+ -->
<!--     lims(y=c(0,1)) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrb_marginal_icc_ov_facet_estimator_model.pdf",plot = p, width=9, height=6, units='in') -->

<!-- p <- ggplot(mydata, aes(x=icc_lv, y=SRMRB))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red') + -->
<!--     facet_grid(Model~Estimator)+ -->
<!--     lims(y=c(0,1)) -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrb_marginal_icc_lv_facet_estimator_model.pdf",plot = p,width=9, height=6, units='in') -->

<!-- ``` -->


<!-- ## Fit distribution by Model and Estimator only -->


<!-- ```{r box-est-model-thing} -->
<!-- p <- ggplot(mydata, aes(x=Model, y=CFI))+ -->
<!--     geom_boxplot()+ -->
<!--     facet_grid(.~Estimator) + -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red')  -->
<!-- p -->
<!-- if(save.fig == T) ggsave("cfi_marginal_model_estimator.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=Model, y=TLI))+ -->
<!--     geom_boxplot()+ -->
<!--     facet_grid(.~Estimator) + -->
<!--     geom_abline(intercept = .95, slope=0, -->
<!--                 linetype='dashed', color = 'red') -->
<!-- p -->
<!-- if(save.fig == T) ggsave("tli_marginal_model_estimator.pdf",plot = p, width=6, height=4, units='in') -->



<!-- p <- ggplot(mydata, aes(x=Model, y=RMSEA))+ -->
<!--     geom_boxplot()+ -->
<!--     facet_grid(.~Estimator) + -->
<!--     geom_abline(intercept = .06, slope=0, -->
<!--                 linetype='dashed', color = 'red')  -->
<!-- p -->
<!-- if(save.fig == T) ggsave("rmsea_marginal_model_estimator.pdf",plot = p, width=6, height=4, units='in') -->



<!-- p <- ggplot(mydata, aes(x=Model, y=SRMRW))+ -->
<!--     geom_boxplot()+ -->
<!--     facet_grid(.~Estimator) + -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red')  -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrw_marginal_model_estimator.pdf",plot = p, width=6, height=4, units='in') -->


<!-- p <- ggplot(mydata, aes(x=Model, y=SRMRB))+ -->
<!--     geom_boxplot()+ -->
<!--     geom_abline(intercept = .08, slope=0, -->
<!--                 linetype='dashed', color = 'red')+ -->
<!--     facet_grid(.~Estimator) + -->
<!--     lims(y=c(0,1))  -->
<!-- p -->
<!-- if(save.fig == T) ggsave("srmrb_marginal_model_estimator.pdf",plot = p, width=6, height=4, units='in') -->


<!-- ``` -->


<!-- ## interaction between Estimator and number of groups -->

<!-- ```{r} -->

<!-- p <- ggplot(mydata, aes(x=ss_l2, y=RMSEA))+ -->
<!--     geom_boxplot()+ -->
<!--     facet_grid(.~Estimator) -->
<!-- p -->

<!-- with(mydata, { -->
<!--   interaction.plot(ss_l2, Estimator, RMSEA,  -->
<!--                    fun = function(x) mean(x, na.rm = TRUE), -->
<!--                    main = "RMSEA Interaction Plot") -->
<!-- }) -->
<!-- ``` -->

<!-- ## Interaction between Estimator and Latent ICC for SRMRW -->

<!-- ```{r} -->

<!-- p <- ggplot(mydata, aes(x=Estimator, y=SRMRW))+ -->
<!--     geom_boxplot()+ -->
<!--     facet_grid(.~icc_lv) -->
<!-- p -->

<!-- with(mydata, { -->
<!--   interaction.plot(icc_lv, Estimator, SRMRW,  -->
<!--                    fun = function(x) mean(x, na.rm = TRUE), -->
<!--                    main = "SRMRW Interaction Plot", ylab="SRMRW") -->
<!-- }) -->
<!-- ``` -->
