---
title: "Convergence, Admissibility, and Fit Descriptive Statistics"
date: "2019-05-07"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---


Purpose of this file:

   1. Summarize convergence
   2. Summarize proper solution rates
   3. Creating simple descriptive statistics across conditions
   4. Generating tables of those stats

The output is mostly just a lot of latex ready tables. Not all of these tables are included in the final publication, but we wanted to be as precise as possible with respect to the summary of the fit statistics.

# Packages and Set-Up

```{r set-up, tidy=T}
##Chunk iptions
knitr::opts_chunk$set(out.width = "225%")

#setwd('C:/Users/noahp/Dropbox/MCFA Thesis/Code Results')

## Packages
## General Packages
library(tidyverse)
# Formatting and Tables
library(kableExtra)
library(xtable)
# For plotting
library(ggplot2)
theme_set(theme_bw())
# Data manipulating
library(dplyr)

```


# Data Management

```{r data, tidy=T}

sim_results <- as_tibble(read.table('data/compiled_fit_results.txt', header=T,sep='\t'))

## Next, turn condition into a factor for plotting
sim_results$Condition <- as.factor(sim_results$Condition)

## Next, since TLI is non-normed, any value greater than 1 needs to be rescaled to 1.
sim_results$TLI <- ifelse(sim_results$TLI > 1, 1, sim_results$TLI)
sim_results$TLI <- ifelse(sim_results$TLI < 0, 0, sim_results$TLI)
## Next, summarize the results of the chi-square test of model fit. This is done simply by comparing the p-value to alpha (0.05) and indicating whether the model was flagged as fitting or not.
# Note: if  p < 0.05 then this variable is flagged as 0, and 1 otherwise
sim_results$Chi2_pvalue_decision <- ifelse(sim_results$chisqu_pvalue < 0.05, 0, 1)
# 0 = rejected that these data fit this model
# 1 = failed to reject that these data fit this model
```

## Adding Labels to Conditions

Currently, each condition is kind of like a hidden id that we don't know what the actual factor is. 
So, first thing isto create meaningful labels for us to use.
Remember, the 72 conditions for the this study were

  1. Level-1 sample size (ss\_l1 or n1) (5, 10, 30)
  2. Level-2 sample size (ss\_l2 or n2) (30, 50, 100, 200)
  3. Observed indicator ICC (.1, .3, .5)
  4. Latent variable ICC (.1, .5)
  
```{r}
## level-1 Sample size
ss_l1 <- c(5, 10, 30) ## 6 conditions each
ss_l2 <- c(30, 50, 100, 200) ## 18 condition each
icc_ov <- c(.1, .3, .5) ## 2 conditions each
icc_lv <- c(.1, .5) ## every other condition
nCon <- 72 # number of conditions
nRep <- 500 # number of replications per condition
nMod <- 12 ## numberof estimated models per conditions
## Total number of rows: 432,000
ss_l2 <- c(rep(ss_l2[1], 18*nRep*nMod), rep(ss_l2[2], 18*nRep*nMod), 
           rep(ss_l2[3], 18*nRep*nMod), rep(ss_l2[4], 18*nRep*nMod))
ss_l1 <- rep(c(rep(ss_l1[1],6*nRep*nMod), rep(ss_l1[2],6*nRep*nMod), rep(ss_l1[3],6*nRep*nMod)), 4)
icc_ov <- rep(c(rep(icc_ov[1], 2*nRep*nMod), rep(icc_ov[2], 2*nRep*nMod), rep(icc_ov[3], 2*nRep*nMod)), 12)
icc_lv <- rep(c(rep(icc_lv[1], nRep*nMod), rep(icc_lv[2], nRep*nMod)), 36)
## Force these vectors to be column vectors
ss_l1 <- matrix(ss_l1, ncol=1)
ss_l2 <- matrix(ss_l2, ncol=1)
icc_ov <- matrix(icc_ov, ncol=1)
icc_lv <- matrix(icc_lv, ncol=1)
## Add the labels to the results data frame
sim_results <- sim_results[order(sim_results$Condition),]
sim_results <- cbind(sim_results, ss_l1, ss_l2, icc_ov, icc_lv)

## Force the conditions to be factors
sim_results$ss_l1 <- as.factor(sim_results$ss_l1)
sim_results$ss_l2 <- as.factor(sim_results$ss_l2)
sim_results$icc_ov <- as.factor(sim_results$icc_ov)
sim_results$icc_lv <- as.factor(sim_results$icc_lv)
sim_results$Model <- factor(sim_results$Model, levels = c('C','M1','M2','M12'), ordered = T)
## Set up iterators for remainder of script
mods <- c('C', 'M1', 'M2', 'M12')
ests <- c('MLR', 'ULSMV', 'WLSMV')
```

For the descriptive statistics, I will use dplyr.
From here I can easily create matrices that store the results so that I can easily print out the results for summarizing the results.
Each will be printed out as a html table and a xtable (latex ready) table.

# Convergence Summary

Convergence will be broken out by Model (C, M1, M2, M12) and estimator (MLR, WLSMV, ULSMV). 
So, there will 12 smallish tables piecemail tables.
Next, one very large table of all the conditions will be exported in latex ready format.

## Convergence by Model and Estimator

```{r}

## first table summary table
c <- sim_results %>%
  group_by(Model, Estimator) %>%
  summarise(Converge=mean(Converge))
# Next make the columns the estimator factor
c <- cbind(c[ c$Model == 'C', 'Converge'], 
           c[ c$Model == 'M1', 'Converge'], 
           c[ c$Model == 'M2', 'Converge'], 
           c[ c$Model == 'M12', 'Converge'])
rownames(c) <- c('MLR', 'ULSMV', 'WLSMV')
colnames(c) <- c('C' ,'M1' ,'M2', 'M12')
## Print results in a nice looking table in HTML
kable(c, format='html') %>%
    kable_styling(full_width = T)%>%
  add_header_above(c(' '= 1, 'Model Specification'=4))
## Print out in tex
print(xtable(c, digits = 3), booktabs = T, include.rownames = T)

```

## Model, Estimator, and Sample Sizes

```{r}

## first table summary table
c <- sim_results %>%
  group_by(Model, Estimator, ss_l1, ss_l2) %>%
  summarise(Converge=mean(Converge))
# Next make the columns the estimator factor
c1 <- cbind(c[ c$Model == 'C', c('Estimator', 'ss_l1', 'ss_l2', 'Converge')], 
           c[ c$Model == 'M1', 'Converge'], 
           c[ c$Model == 'M2', 'Converge'], 
           c[ c$Model == 'M12', 'Converge'])
colnames(c1) <- c('Estimator', 'SS Level-1', 'SS Level-2', 'C' ,'M1' ,'M2', 'M12')

## Print results in a nice looking table in HTML
kable(c1, format='html') %>%
  kable_styling(full_width = T) %>%
  add_header_above(c(' '= 3, 'Model Specification'=4))
## Print out in tex
print(xtable(c1, digits = 3), booktabs = T, include.rownames = F)

```

## Across all conditions

```{r}

## first table summary table
c <- sim_results %>%
  group_by(Model, Estimator, ss_l1, ss_l2, icc_ov, icc_lv) %>%
  summarise(Converge=mean(Converge))
# Next make the columns the estimator factor
c1 <- cbind(c[ c$Model == 'C' & c$Estimator == 'MLR', c('ss_l1', 'ss_l2','icc_ov', 'icc_lv', 'Converge')],
            c[ c$Model == 'C' & c$Estimator == 'ULSMV', 'Converge'],
            c[ c$Model == 'C' & c$Estimator == 'WLSMV', 'Converge'],
            c[ c$Model == 'M1' & c$Estimator == 'MLR', 'Converge'], 
            c[ c$Model == 'M1' & c$Estimator == 'ULSMV', 'Converge'],
            c[ c$Model == 'M1' & c$Estimator == 'WLSMV', 'Converge'],
            c[ c$Model == 'M2' & c$Estimator == 'MLR', 'Converge'],
            c[ c$Model == 'M2' & c$Estimator == 'ULSMV', 'Converge'],
            c[ c$Model == 'M2' & c$Estimator == 'WLSMV', 'Converge'],
            c[ c$Model == 'M12' & c$Estimator == 'MLR', 'Converge'],
            c[ c$Model == 'M12' & c$Estimator == 'ULSMV', 'Converge'],
            c[ c$Model == 'M12' & c$Estimator == 'WLSMV', 'Converge'])
colnames(c1) <- c('SS Level-1', 'SS Level-2', 'ICC-OV', 'ICC-LV', rep(c('MLR', 'ULSMV', 'WLSMV'), 4))

## Print results in a nice looking table in HTML
kable(c1, format='html') %>%
  kable_styling(full_width = T) %>%
  add_header_above(c(' '= 4, 'Model C'=3, 'Model M1'=3, 'Model M2'=3, 'Model M12'=3))
## Print out in tex
print(xtable(c1, digits = 3), booktabs = T, include.rownames = F)

```



# Admissibility Summary

Admissibility rates are first subsetted to the converged models. 
So, the rates may seem misleading and not directly relatable across all conditions and models due to differences in convergence rates.

```{r}

c.sim_results <- filter(sim_results, Converge == 1)

```

## Admissibilty by Model and Estimator

```{r}

## first table summary table
c <- c.sim_results %>%
  group_by(Model, Estimator) %>%
  summarise(Admissible=mean(Admissible))
# Next make the columns the estimator factor
c1 <- cbind(c[ c$Model == 'C', 'Admissible'], 
           c[ c$Model == 'M1', 'Admissible'], 
           c[ c$Model == 'M2', 'Admissible'], 
           c[ c$Model == 'M12', 'Admissible'])
rownames(c1) <- c('MLR', 'ULSMV', 'WLSMV')
colnames(c1) <- c('C' ,'M1' ,'M2', 'M12')
## Print results in a nice looking table in HTML
kable(c1, format='html') %>%
    kable_styling(full_width = T) %>%
    add_header_above(c(' '= 1, 'Model Specification'=4))
  
## Print out in tex
print(xtable(c1, digits = 3), booktabs = T, include.rownames = T)

```

## Model, Estimator, and Sample Sizes

```{r}

## first table summary table
c <- c.sim_results %>%
  group_by(Model, Estimator, ss_l1, ss_l2) %>%
  summarise(Admissible=mean(Admissible))
# Next make the columns the estimator factor
c1 <- cbind(c[ c$Model == 'C', c('Estimator', 'ss_l1', 'ss_l2', 'Admissible')], 
           c[ c$Model == 'M1', 'Admissible'], 
           c[ c$Model == 'M2', 'Admissible'], 
           c[ c$Model == 'M12', 'Admissible'])
colnames(c1) <- c('Estimation', 'SS Level-1', 'SS Level-2', 'C' ,'M1' ,'M2', 'M12')

## Print results in a nice looking table in HTML
kable(c1, format='html') %>%
  kable_styling(full_width = T) %>%
  add_header_above(c(' '= 3, 'Model Specification'=4))
## Print out in tex
print(xtable(c1, digits = 3), booktabs = T, include.rownames = F)

```

## Across all conditions

```{r}

## first table summary table
c <- c.sim_results %>%
  group_by(Model, Estimator, ss_l1, ss_l2, icc_ov, icc_lv) %>%
  summarise(Admissible=mean(Admissible))
# Next make the columns the estimator factor
c1 <- cbind(c[ c$Model == 'C' & c$Estimator == 'MLR', c('ss_l1', 'ss_l2','icc_ov', 'icc_lv', 'Admissible')],
            c[ c$Model == 'C' & c$Estimator == 'ULSMV', 'Admissible'],
            c[ c$Model == 'C' & c$Estimator == 'WLSMV', 'Admissible'],
            c[ c$Model == 'M1' & c$Estimator == 'MLR', 'Admissible'], 
            c[ c$Model == 'M1' & c$Estimator == 'ULSMV', 'Admissible'],
            c[ c$Model == 'M1' & c$Estimator == 'WLSMV', 'Admissible'],
            c[ c$Model == 'M2' & c$Estimator == 'MLR', 'Admissible'],
            c[ c$Model == 'M2' & c$Estimator == 'ULSMV', 'Admissible'],
            c[ c$Model == 'M2' & c$Estimator == 'WLSMV', 'Admissible'],
            c[ c$Model == 'M12' & c$Estimator == 'MLR', 'Admissible'],
            c[ c$Model == 'M12' & c$Estimator == 'ULSMV', 'Admissible'],
            c[ c$Model == 'M12' & c$Estimator == 'WLSMV', 'Admissible'])
colnames(c1) <- c('SS Level-1', 'SS Level-2', 'ICC-OV', 'ICC-LV', rep(c('MLR', 'ULSMV', 'WLSMV'), 4))

## Print results in a nice looking table in HTML
kable(c1, format='html') %>%
  kable_styling(full_width = T) %>%
  add_header_above(c(' '= 4, 'Model C'=3, 'Model M1'=3, 'Model M2'=3, 'Model M12'=3))
## Print out in tex
print(xtable(c1, digits = 3), booktabs = T, include.rownames = F)

```


# Descriptive Statistics of Fit Indices

Now for the long process of making tables for the MANY conditions for the descriptive statistics.
For this, we need to do this is steps so that all the information gets outputted in the correct manor for table.
For each statistic under each condition, model, and estimator, the code below create a table that contains the average value and the standard deviation.
Again, just like the descriptives above, a summary table was made to start.

These tables are made based only on the 1) converged models and 2) the admissible solutions.

The fit indices included are:

  1. Chi-square p-value summary, i.e. proportion of tims the p-value was greater than 0.05. No SD is reported here.
  2. CFI with mean and sd
  3. TLI with mean and sd
  4. RMSEA with mean and sd
  5. SRMRW with mean and sd
  6. SRMRB with mean and sd

```{r fit-sum}

mydata <- filter(sim_results, Converge == 1 & Admissible == 1)

## first table summary table
a <- mydata %>%
  group_by(Model, Estimator) %>%
  summarise(
    chi2=mean(Chi2_pvalue_decision, na.rm = T),
    CFI.m =mean(CFI, na.rm = T), CFI.sd =sd(CFI, na.rm = T),
    TLI.m =mean(TLI, na.rm = T), TLI.sd =sd(TLI, na.rm = T),
    RMSEA.m =mean(RMSEA, na.rm = T), RMSEA.sd =sd(RMSEA, na.rm = T),
    SRMRW.m =mean(SRMRW, na.rm = T), SRMRW.sd =sd(SRMRW, na.rm = T),
    SRMRB.m =mean(SRMRB, na.rm = T), SRMRB.sd =sd(SRMRB, na.rm = T)
  )
## Print results in a nice looking table in HTML
kable(a, format='html') %>%
    kable_styling(full_width = T)

## make a copy of a to print into
a1 <- as_tibble(as.data.frame(matrix(NA, ncol=8,nrow=nrow(a))))
colnames(a1) <- c('Model', 'Estimation', "chi2", "CFI",'TLI', 'RMSEA', 'SRMRW', 'SRMRB')
i <- 1
for(i in 1:nrow(a)){
  a1[i,3:8] <- unlist(c(
    round(a[i,3],3),
  paste0(round(a[i,4],3), ' (', round(a[i,5],2), ')'),
  paste0(round(a[i,6],3), ' (', round(a[i,7],2), ')'),
  paste0(round(a[i,8],3), ' (', round(a[i,9],2), ')'),
  paste0(round(a[i,10],3), ' (', round(a[i,11],2), ')'),
  paste0(round(a[i,12],3), ' (', round(a[i,12],2), ')')
  ))
}
a1[,1:2] <- a[,1:2]## add factors back
## Print out in tex
print(xtable(a1, digits = 3), booktabs = T, include.rownames = F)

```

## Fit statistics by Model, Estimation Method, and Sample Size Conditions

An interesting additonal column is added called Prop.Use, which is the total proportion of usable replications for each marginal cell of the design. 
Each row of the following table represents the marginal distribution of each fit statistic over the ICC conditions. 
The total number of possible replications is 3000 (500 rep. $\times$6 conditions).
This gives a rough account of the admissibility of the estimation method across sample sizes. 

```{r}


mydata <- filter(sim_results, Converge == 1 & Admissible == 1)

## first table summary table
a <- mydata %>%
  group_by(Model, Estimator, ss_l2, ss_l1) %>%
  summarise(
    Prop.Use=n()/3000,
    chi2=mean(Chi2_pvalue_decision, na.rm = T),
    CFI.m =mean(CFI, na.rm = T), CFI.sd =sd(CFI, na.rm = T),
    TLI.m =mean(TLI, na.rm = T), TLI.sd =sd(TLI, na.rm = T),
    RMSEA.m =mean(RMSEA, na.rm = T), RMSEA.sd =sd(RMSEA, na.rm = T),
    SRMRW.m =mean(SRMRW, na.rm = T), SRMRW.sd =sd(SRMRW, na.rm = T),
    SRMRB.m =mean(SRMRB, na.rm = T), SRMRB.sd =sd(SRMRB, na.rm = T)
  )
## Print results in a nice looking table in HTML
kable(a, format='html') %>%
    kable_styling(full_width = T)

## make a copy of a to print into
a1 <- as_tibble(as.data.frame(matrix(NA, ncol=11,nrow=nrow(a))))
colnames(a1) <- c('Model', 'Estimation', "N2", "N1", "Prop.Use", "chi2", "CFI",'TLI', 'RMSEA', 'SRMRW', 'SRMRB')
i <- 1
for(i in 1:nrow(a)){
  a1[i,5:11] <- unlist(c(
  round(a[i,5],3), round(a[i,6],3),
  paste0(round(a[i,7],3), ' (', round(a[i,8],2), ')'),
  paste0(round(a[i,9],3), ' (', round(a[i,10],2), ')'),
  paste0(round(a[i,11],3), ' (', round(a[i,12],2), ')'),
  paste0(round(a[i,13],3), ' (', round(a[i,14],2), ')'),
  paste0(round(a[i,15],3), ' (', round(a[i,16],2), ')')
  ))
}
a1[,1:4] <- a[,1:4]## add factors back
## Print out in tex
print(xtable(a1, digits = 3), booktabs = T, include.rownames = F)

```

## TONS of additional tables of the fit statistics across conditions

```{r}
## Now, create MANY subset tables to breakdown these relationships
## loop around these iterators
for(M in mods){
  for(E in ests){
    ### subset tothe model (M) and estimator (E)
    #M <- 'C'
    #E <- 'MLR'
    cat('\n\n ===============================\n')
    cat('\nModel:\t', M)
    cat('\nEstimator:\t', E, '\n')
    sub_dat <- mydata[ mydata$Model == M & mydata$Estimator == E,]

    a <- sub_dat %>%
        group_by(ss_l1, ss_l2, icc_ov, icc_lv) %>%
        summarise(
          N = n(),
          chi2=mean(Chi2_pvalue_decision, na.rm = T),
          CFI.m =mean(CFI, na.rm = T), CFI.sd =sd(CFI, na.rm = T),
          TLI.m =mean(TLI, na.rm = T), TLI.sd =sd(TLI, na.rm = T),
          RMSEA.m =mean(RMSEA, na.rm = T), RMSEA.sd =sd(RMSEA, na.rm = T),
          SRMRW.m =mean(SRMRW, na.rm = T), SRMRW.sd =sd(SRMRW, na.rm = T),
          SRMRB.m =mean(SRMRB, na.rm = T), SRMRB.sd =sd(SRMRB, na.rm = T)
        )
    #print(xtable(a, digits = 3), booktabs = T, include.rownames = F)
    ## Now, create subsets of this results matrix for outputting into small(ish) tables
    ## Subset by ICC conditions
    ICCO <- unique(a$icc_ov)
    ICCL <- unique(a$icc_lv)
    icco <- ICCO[1]
    iccl <- ICCL[1]
    for(icco in ICCO){
      for(iccl in ICCL){
        ### subset tothe model (M) and estimator (E)
        #M <- 'C'
        #E <- 'MLR'
        cat('\n===============================\n')
        cat('\nModel:\t', M)
        cat('\nEstimator:\t', E)
        cat('\nICC Obs. Var.:\t', icco)
        cat('\nICC Lat. Var.:\t', iccl,'\n')
        a_s <- filter(a, icc_ov == icco, icc_lv == iccl)
        ## make a copy of a to print into
        a1 <- as_tibble(as.data.frame(matrix(NA, ncol=9,nrow=nrow(a_s))))
        colnames(a1) <- c('N2', 'N1', 'Num_Rep', "chi2", "CFI",'TLI', 'RMSEA', 'SRMRW', 'SRMRB')
        i <- 1
        for(i in 1:nrow(a_s)){
          a1[i,3:9] <- unlist(c(
            round(a_s[i,5],2),
            round(a_s[i,6],2),
            paste0(round(a_s[i,7],2), '(', round(a_s[i,8],2), ')'),
            paste0(round(a_s[i,9],2), '(', round(a_s[i,10],2), ')'),
            paste0(round(a_s[i,11],2), '(', round(a_s[i,12],2), ')'),
            paste0(round(a_s[i,13],2), '(', round(a_s[i,14],2), ')'),
            paste0(round(a_s[i,15],2), '(', round(a_s[i,16],2), ')')
          ))
        }
        a1[,1:2] <- a_s[,c(2,1)]## add factors back with diff. order
        ## Print out in tex
        print(xtable(a1,
                     caption = paste0('Summary of Fit Statistics Across Conditions: Model ',
                                      M,', Estimator ',E,', ICC_O ',icco,' and ICC_L ', iccl)), 
              booktabs = T, include.rownames = F)
      }
    }## End subset table printing
  }
} ## End loops..

```

